---
title: "FictionEro - Study 1"
editor: source
editor_options: 
  chunk_output_type: console
format:
  html:
    toc: true
    code-fold: true
    self-contained: false
execute: 
  cache: false
  cache-lazy: false
---

# Data Preparation

```{r libraries}
#| message: false
#| warning: false

library(dplyr)
library(tidyverse)
library(easystats)
library(patchwork)
library(ggside)
library(gt)
library(ggdist)
library(posterior)
library(forcats)

options(mc.cores = parallel::detectCores(),
        brms.backend = "cmdstanr",
        width = 300)
```

```{r functions}

results_table <- function(model, effects="fixed", filter=NULL) {
  if("marginaleffects" %in% class(model)) {
    model |> 
      parameters::parameters() |> 
      as.data.frame() |> 
      select(-Parameter, -SE, -S, z=Statistic) |> 
      insight::format_table() |> 
      parameters::display()
  } else {
    display(parameters::parameters(model, effects=effects, keep=filter))
  }
}

# Parameters tables for the models 
params_table <- function(m) {
  # d <- as.data.frame(m, variable = insight::find_parameters(m, effects = "fixed", flatten  = TRUE))
  t <- bayestestR::describe_posterior(m, effects = "fixed", component = "all", ci_method = "hdi", test = "p_direction")
  out <- insight::format_table(t)
  out |> 
    mutate(col = t$pd) |> 
    gt::gt() |> 
    gt::data_color(columns = "col", method = "numeric", target_columns = "pd", 
                   row = col > 0.95, palette = "yellow") |> 
    gt::data_color(columns = "col", method = "numeric", target_columns = "pd", 
                   row = col > 0.97, palette = "green") |> 
    gt::cols_hide("col")
}

# Random effects table
table_dvour <- function(g) {
  performance::performance_dvour(g) |> 
    arrange(desc(D_vour)) |> 
    gt::gt() |> 
    gt::data_color("D_vour", palette = c("red","green"), domain = c(0, 1)) |> 
    gt::fmt_auto()
}

```

```{r data study1}
#| message: false
#| warning: false

dfsub1 <- read.csv("https://raw.githubusercontent.com/RealityBending/FictionEro/refs/heads/main/study1/data/data_participants.csv")
df1 <- read.csv("https://raw.githubusercontent.com/RealityBending/FictionEro/refs/heads/main/study1/data/data.csv") |> 
  right_join(
    select(dfsub1, Participant, Sample, Language, Mobile, starts_with("Feedback_"), 
           BAIT_Visual, BAIT_Text, AI_Knowledge, SexualActivity, 
           GAAIS_Negative, GAAIS_Positive, Porn, COPS_Frequency_2,
           Screen_Size,
           -Feedback_Comments, Country),
    by = "Participant") |> 
  rename(Gender = Sex) |>
  datawizard::rescale(select=c("Valence"), range=c(-1, 1), to=c(0, 1)) |> 
  mutate(Condition = fct_recode(Condition, "Photograph" = "Photograph", "AIGenerated" = "AI-Generated"),
         Condition = fct_relevel(Condition, "Photograph", "AIGenerated"),
         Relevance = fct_recode(Relevance,  "Relevant" = "Relevant",  "Irrelevant"= "Irrelevant", "NonErotic" = "Non-erotic"),
         Relevance =  fct_relevel(Relevance, "Relevant", "Irrelevant", "NonErotic"),
         Gender =  fct_relevel(Gender, "Male", "Female"),
         ConditionBelief = case_when(
           Condition == "Photograph" & Realness > 0.5 ~ "True",
           Condition == "AIGenerated" & Realness < 0.5 ~ "True",
           .default = "False"),
         ConditionBelief = as.factor(ConditionBelief),
         ConditionBelief = fct_relevel(ConditionBelief, "True", "False"),
         PornFrequency = as.numeric(as.factor(COPS_Frequency_2)),
         SexualActivity_num = as.numeric(as.factor(SexualActivity)),
         across(starts_with("Feedback_"), function(x) {fct_relevel(x, "False", "True")}))
```

# Questionnaires

::: panel-tabset
## GAAIS

```{r}
#| message: false
#| warning: false
#| output: false

GAAIS_Negative <- dfsub1[grepl("^GAAIS_Negative_", names(dfsub1))]
GAAIS_Positive <- dfsub1[grepl("^GAAIS_Positive_", names(dfsub1))]

GAAIS_Negative_o <- psych::omega(GAAIS_Negative, n_factors= 1)
GAAIS_Positive_o <- psych::omega(GAAIS_Positive, n_factors= 1)

```

McDonald's Omega (⍵) total was acceptable for both dimensions of the GAAIS (Negative ⍵ = `r round(GAAIS_Negative_o$omega.tot,2)`, and Positive ⍵ = `r round(GAAIS_Positive_o$omega.tot,2)`).

## BAIT

```{r}
#| message: false
#| warning: false
#| output: false



dfsub1$BAIT_8_TextIssues <- 1- dfsub1$BAIT_8_TextIssues
dfsub1$BAIT_2_ImagesIssues <- 1- dfsub1$BAIT_2_ImagesIssues
dfsub1$BAIT_4_VideosIssues <- 1- dfsub1$BAIT_4_VideosIssues
# dfsub1$BAIT_5_ImitatingReality <- dfsub1$BAIT_5_ImitatingReality


BAIT_Text <- dfsub1[, grepl("^BAIT_[78]_Text", names(dfsub1))]
BAIT_Images <- dfsub1[, grepl("^BAIT_[12]_Images", names(dfsub1))]
BAIT_Videos <- dfsub1[,grepl("^BAIT_[34]_Videos", names(dfsub1))]
BAIT_Enviornment <-dfsub1[, grepl("^BAIT_[56]", names(dfsub1))]


BAIT_Text_a <- psych::alpha(BAIT_Text)
BAIT_Images_a <- psych::alpha(BAIT_Images)
BAIT_Videos_a <- psych::alpha(BAIT_Videos)
BAIT_Enviornment_a <- psych::alpha(BAIT_Enviornment)
```

Cronbach's alpha (⍺) was questionable for the Text dimension (⍺ = `r round(BAIT_Text_a$total$raw_alpha,2)`), very poor for the Images dimension (⍺ = `r round(BAIT_Images_a$total$raw_alpha, 2)`), poor for the Videos (⍺ = `r round(BAIT_Videos_a$total$raw_alpha, 2)`) and poor for the Environment dimensions (⍺ = `r round(BAIT_Enviornment_a$total$raw_alpha, 2)`).

## COPS

```{r}
#| output: false

dfsub1 <- dfsub1 |>
  mutate(COPS_Duration_1 = case_when(
    COPS_Duration_1 =="1. Less than 5 minutes" ~ 1,
    COPS_Duration_1 == "2. 6-15 minutes" ~2, 
    COPS_Duration_1 =="3. 16-25 minutes" ~3, 
    COPS_Duration_1 == "4. 26-35 minutes" ~ 4,
    COPS_Duration_1 == "5. 36-45 minutes" ~5, 
    COPS_Duration_1 == "6. 46+ minutes" ~ 6),
    COPS_Frequency_2 = case_when(
    COPS_Frequency_2 == "0. I haven't viewed pornography in the past 30 days" ~ 0, 
    COPS_Frequency_2 =="1. I viewed pornography once in the past 30 days" ~ 1,
    COPS_Frequency_2 == "2. I viewed pornography twice in the past 30 days" ~2, 
    COPS_Frequency_2 =="3. I viewed pornography weekly" ~3, 
    COPS_Frequency_2 == "4. I viewed pornography multiple times a week " ~ 4,
    COPS_Frequency_2 == " 5. I viewed pornography daily" ~5, 
    COPS_Frequency_2 == "6. I viewed pornography multiple times a day" ~ 6),
    SexualActivity = case_when(
      SexualActivity == "1. Less than 24h ago" ~ 1 , 
      SexualActivity == "2. Within the last 3 days" ~ 2, 
      SexualActivity == "3. Within the last week" ~ 3,
      SexualActivity == "4. Within the last month" ~ 4, 
      SexualActivity == "5. Within the last year" ~ 5,
      SexualActivity == "6. More than a year ago" ~ 5)
    )

COPS <- select(dfsub1, starts_with("COPS_Frequency_"), starts_with("COPS_Duration_1"), "SexualActivity")

COPS_o <- psych::omega(COPS, nfactors = 1)
```

McDonald's Omega (⍵) total was poor for the (⍵ =COPS `r round(COPS_o$omega.tot,2)`).
:::

# Manipulation Checks

```{r ratebelief 1}
#| message: false
#| warning: false

rate1 <- table(df1$Feedback_LabelsIncorrect)["True"] / sum(table(df1$Feedback_LabelsIncorrect))
```

The rate of people that did not believe the instructions in study 1 (i.e., gave feedback that the labels were incorrect) was `r round(mean(rate1) * 100, 1)`%.

```{r}
inc <- table(df1$ConditionBelief)["True"] /sum(table(df1$ConditionBelief))
```

The number of incongruent trials (i.e., pictures presented as photos/AI-generated in task 1 but believed to be to the other category during phase 2) was `r round(mean(inc) * 100, 1)`%.


::: panel-tabset
## Arousal 

<!-- Arousal ratings are heavily skewed towards the lower end of the scale, with a much higher frequency of scores at 0 and a slight increase in the middle of the scale, for both images presented as AI-Generated and Photograph.  -->

```{r dist arousal 1}
#| message: false
#| warning: false
#| fig-width: 12

arousal_dist1 <- df1 |>
  ggplot(aes(x=Arousal, fill = Condition)) +
  geom_histogram(position = "identity", alpha = 0.5, colour = "black", bins = 30) +
  scale_x_continuous(breaks = c(0, 1)) +
  labs(title = "Arousal Study 1", ) +
  facet_wrap(~Gender) +
  scale_fill_manual(values=c("AIGenerated"="#2196F3", "Photograph"="#F44336")) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5, face="bold"))


arousal_dist1
```

<!-- Arousal ratings for AI vs photos are similar overall, with those who said AI is less arousing showing slightly lower (more negative) differences. -->

```{r arousal 1 t_test}
#| message: false
#| warning: false

dfsub1_arousal <- dfsub1 |>
  right_join(
    df1 |>
      group_by(Participant, Condition) |>
      summarise(mean_arousal = mean(Arousal, na.rm = TRUE),.groups = "drop") |>
      pivot_wider(
        names_from = Condition,
        names_prefix = "mean_Arousal_",
        values_from = mean_arousal) |>
      mutate(diff_arousal = `mean_Arousal_AIGenerated` - mean_Arousal_Photograph)) |>
  mutate(Feedback_AILessArousing = as.factor(Feedback_AILessArousing)) |>
  as.data.frame()

df1 |>
  group_by(Feedback_AILessArousing, Condition ) |>
  summarise(mean_Arousal = mean(Arousal, na.rm = TRUE), 
            sd_Arousal = sd(Arousal, na.rm = TRUE),.groups = "drop") |>
  gt() |>
  fmt_number(decimals = 3, use_seps = FALSE)

ttest_less_arousal <- BayesFactor::ttestBF(dfsub1_arousal$diff_arousal, dfsub1_arousal$Feedback_AILessArousing)

model_parameters(ttest_less_arousal)

```

```{r arousal 1 diff plot}
#| message: false
#| warning: false
#| fig-width: 12

diff_plot1 <- dfsub1_arousal |> 
  ggplot(aes(x = Feedback_AILessArousing, y = diff_arousal, fill = Feedback_AILessArousing)) +
  geom_boxplot(width = 0.4,alpha = 0.7) +
  geom_jitter(width = 0.2, alpha = 0.1, size = 1) +
  stat_summary(fun = mean, geom = "point", shape = 23, size = 2, fill = "black") +
  labs(
    title = "Study 1",
    x = "Participant said AI is less arousing",
    y = "Arousal Difference (AI - Photo)"
  ) +
  scale_fill_manual(values = c("True" = "#E66100", "False" = "#5D3A9B")) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    legend.position = "none"
  )

diff_plot1
```


## Enticement
<!-- Like in Arousal, Enticing ratings are heavily skewed towards the lower end of the scal and a slight increase in the middle of the scale. -->

```{r dist enticement 1}
#| fig-width: 12
enticement_dist1 <- df1 |>
  ggplot(aes(x=Enticement, fill = Condition)) +
  geom_histogram(position = "identity", alpha = 0.5, colour = "black", bins = 30) +
  scale_x_continuous(breaks = c(0, 1)) +
  labs(title = "Enticement Study 1", ) +
  facet_wrap(~Gender) +
  scale_fill_manual(values=c("AIGenerated"="#2196F3", "Photograph"="#F44336")) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5, face="bold"))


enticement_dist1
```

<!-- Enticement ratings for AI vs photos are similar overall, with those who said AI is less arousing showing slightly lower (more negative) differences. -->

```{r enticement 1 t_test}
#| message: false


dfsub1_enticement <- dfsub1 |>
  right_join(
    df1 |>
      group_by(Participant, Condition) |>
      summarise(mean_enticement = mean(Enticement, na.rm = TRUE),.groups = "drop") |>
      pivot_wider(
        names_from = Condition,
        names_prefix = "mean_Enticement_",
        values_from = mean_enticement) |>
      mutate(diff_enticement = `mean_Enticement_AIGenerated` - mean_Enticement_Photograph)) |>
  mutate(Feedback_AILessArousing = as.factor(Feedback_AILessArousing)) |>
  as.data.frame()

df1 |>
  group_by(Feedback_AILessArousing, Condition ) |>
  summarise(mean_Enticement = mean(Enticement, na.rm = TRUE), 
            sd_Enticement = sd(Enticement, na.rm = TRUE),.groups = "drop") |>
  gt() |>
  fmt_number(decimals = 3,
    use_seps = FALSE)

ttest1 <- BayesFactor::ttestBF(dfsub1_enticement$diff_enticement, dfsub1_enticement$Feedback_AILessArousing)

model_parameters(ttest1)
```

```{r enticement 1 diff plot}
diff_plot1 <- dfsub1_enticement |> 
  ggplot(aes(x = Feedback_AILessArousing, y = diff_enticement, fill = Feedback_AILessArousing)) +
  geom_boxplot(width = 0.4,alpha = 0.7) +
  geom_jitter(width = 0.2, alpha = 0.1, size = 1) +
  stat_summary(fun = mean, geom = "point", shape = 23, size = 2, fill = "black") +
  labs(
    title = "Study 1",
    x = "Participant said AI is less arousing",
    y = "Enticement Difference (AI - Photo)"
  ) +
  scale_fill_manual(values = c("True" = "#E66100", "False" = "#5D3A9B")) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    legend.position = "none"
  )

diff_plot1
```


## Valence 

```{r dist valence 1}
#| fig-width: 12
valence_dist1 <- df1 |>
  ggplot(aes(x=Valence, fill = Condition)) +
  geom_histogram(position = "identity", alpha = 0.5, colour = "black", bins = 30) +
  scale_x_continuous(breaks = c(0, 1)) +
  labs(title = "Valence Study 1", ) +
  facet_wrap(~Gender) +
  scale_fill_manual(values=c("AIGenerated"="#2196F3", "Photograph"="#F44336")) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5, face="bold"))


valence_dist1
```

```{r valence 1 t_test}
#| message: false

dfsub1_valence <- dfsub1 |>
  right_join(
    df1 |>
      group_by(Participant, Condition) |>
      summarise(mean_Valence = mean(Valence, na.rm = TRUE), .groups = "drop") |>
      pivot_wider(
        names_from = Condition,
        names_prefix = "mean_Valence_",
        values_from = mean_Valence) |>
      mutate(diff_valence = `mean_Valence_AIGenerated` - mean_Valence_Photograph)) |>
  mutate(Feedback_AILessArousing = as.factor(Feedback_AILessArousing)) |>
  as.data.frame()

df1 |>
  group_by(Feedback_AILessArousing, Condition ) |>
  summarise(mean_Valence = mean(Valence, na.rm = TRUE), 
            sd_valence = sd(Valence, na.rm = TRUE),.groups = "drop") |>
  gt() |>
  fmt_number(decimals = 3, use_seps = FALSE)

ttest1 <- BayesFactor::ttestBF(dfsub1_valence$diff_valence, dfsub1_valence$Feedback_AILessArousing)

model_parameters(ttest1)
```

```{r valence 1 diff plot}
diff_plot1 <- dfsub1_valence |> 
  ggplot(aes(x = Feedback_AILessArousing, y = diff_valence, fill = Feedback_AILessArousing)) +
  geom_boxplot(width = 0.4,alpha = 0.7) +
  geom_jitter(width = 0.2, alpha = 0.1, size = 1) +
  stat_summary(fun = mean, geom = "point", shape = 23, size = 2, fill = "black") +
  labs(
    title = "Study 1",
    x = "Participant said AI is less arousing",
    y = "Valence Difference (AI - Photo)"
  ) +
  scale_fill_manual(values = c("True" = "#E66100", "False" = "#5D3A9B")) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    legend.position = "none"
  )

diff_plot1
```

:::

# Models 

::: panel-tabset

## Arousal

```{r arousal 1 by condition belief plot }
#| message: false
#| warning: false

df1 |> 
  ggplot(aes(x = Gender, y = Arousal, fill = ConditionBelief)) +
  geom_violin(position = position_dodge(width = 1), alpha = 0.7, trim = FALSE) +
  stat_pointinterval(position = position_dodge(width = 1),point_size = 1.5) +
  facet_grid(Relevance ~ Condition) +
  scale_fill_manual(values = c("True" = "#E66100", "False" = "#5D3A9B")) +
  theme_minimal(base_size = 14) +
  labs(subtitle ="Study 1", x = "Gender",y = "Arousal",fill = "Congruence")
```

```{r arousal 1 model load}

m <- readRDS("models/ZOIB/ModelArousal_1_ZOIB.rds")
```

<!-- Females reported lower arousal than males. Arousal was highest for relevant images and lowest for non-erotic images, with smaller relevance effects among females. Labeling images as AI-generated was associated with reduced arousal, strongest for relevant content and minimal for non-erotic images (especially among females). -->

<!-- Participants who maintained label congruency across phases reported higher arousal than those who changed labels; this effect was larger for males. Label incongruency showed small positive deviations in some conditions (most notably for AI-labeled relevant images and, to a lesser extent, for irrelevant and non-erotic images) with generally larger deviations among females. -->

```{r arousal 1 model analysis}
#| message: false
#| warning: false

params_table(m)
summary(m, robust = TRUE)
#performance::performance(m)
```

### Marginal contrasts

::: panel-tabset
#### Effect of Relevance

```{r arousal est cont relevance}
#| message: false
#| warning: false

estimate_contrasts(m, contrast = "Relevance", by="Gender", backend = "emmeans") 

```


```{r}
#estimate_contrasts(m, contrast = "Condition", by=c("Gender", "Relevance"), comparison = "(b1 - b7) = (b2 - b8)") 

```

#### Effect of Condition 

```{r arousal est cont condition }
#| message: false
#| warning: false

#estimate_contrasts(m, contrast = "Condition", by=c("Gender", "Relevance"), backend = "emmeans") 

```


```{r arousal 1 model plot cond}
#| message: false
#| warning: false

pred_a2 <- modelbased::estimate_means(m, by=c("Gender", "Relevance", "Condition"), backend = "emmeans") |>
  as.data.frame()

pred_a2 |>
  mutate(Gender = fct_relevel(Gender, "Male", "Female")) |>
  ggplot(aes(x=Relevance, y=Probability)) +
    geom_hline(yintercept=0, color="darkgrey") +
  geom_line(aes(group=Condition, color=Condition), position = position_dodge(width=0.4), alpha=0.8, linewidth=0.2) +
  geom_pointrange(aes(ymin = CI_low, ymax=CI_high, color=Condition), position = position_dodge(width=0.4), size=0.6) +
 # geom_text(data=pd, aes(y=y, label = label), hjust=0.5, size = 3.5) +
 # geom_text(data=pd_small, aes(y=y, label = label), hjust=0.5, size = 2.5) +
  geom_rect(data=data.frame(Probability=0.1, Gender=as.factor("Male"), Relevance="Relevant"),
            aes(xmin=0.6, xmax=1.4, ymin=0.5, ymax=0.65), color="#8BC34A", alpha=0, linewidth =1.2 ) +
   geom_rect(data=data.frame(Probability=0.1, Gender=as.factor("Female"), Relevance="Relevant"),
            aes(xmin=0.6, xmax=1.4, ymin=0.30, ymax=0.45), color="#8BC34A", alpha=0, linewidth =1.2 ) +
  facet_grid(~Gender, switch = "y") +
  scale_y_continuous(limits=c(0, 0.7), labels=scales::percent) +
  scale_color_manual(values=c("AIGenerated"="#2196F3", "Photograph"="#F44336")) +
  theme_minimal() +
    theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        axis.text.y = element_text(size = 10, face = "bold"),
        strip.placement = "outside",
        strip.background.x = element_rect(fill=c("lightgrey"), color=NA),
        strip.text.x = element_text(size = 12, face = "bold"),
        strip.text.y = element_text(size = 10, face = "bold"),
        axis.text.x = element_text(angle=25, hjust=1, vjust=1.1, size=10, color="black"),
        legend.text = element_text(size = 10),
        legend.position = "bottom") +
  labs(color="Images presented as:")

```

```{r}
#modelbased::estimate_means(m, by=c("Gender", "Relevance", "Condition"), backend = "emmeans")

#estimate_contrasts(m, c("Gender", "Relevance", "Condition"), comparison = "(b1 - b7) = (b2 - b8)", backend = "emmeans") 
```


#### Effect of Condition depending on congruency

<!-- When participants maintained label concistency across phases, photographs were rated as more arousing than AI-generated images, particularly for relevant content. When labels were not maintained, this pattern reversed for relevant images, with AI-generated images rated as more arousing, while effects for irrelevant and non-erotic images were small or uncertain. Gender differences were modest.  -->

```{r arousal est cont congruency}
#| message: false
#| warning: false

estimate_contrasts(m, contrast = "Condition", by=c("Gender", "Relevance", "ConditionBelief"), backend = "emmeans") 
```

```{r arousal 1 model plot}
#| message: false
#| warning: false

pred_a3 <- modelbased::estimate_means(m, by=c("Gender", "Relevance", "Condition", "ConditionBelief"), backend = "emmeans") |>
  as.data.frame()

pd <- data.frame(label=c("pd = 100%", "pd = 100%", "pd = 100%", "pd = 100%"),
                 Gender = c("Male", "Female", "Male", "Female"),
                 ConditionBelief = c("Congruent", "Congruent", "Incongruent", "Incongruent"),
                 Relevance = c("Relevant", "Relevant", "Relevant", "Relevant"),
                 y =c(0.80, 0.55, 0.75, 0.55))

pd_small <- data.frame(label=c("pd = 99.50%", "pd = 99.66%", "pd = 99.69%"),
                 Gender = c("Female", "Male", "Female"),
                 ConditionBelief = c("Congruent", "Congruent", "Incongruent"),
                 Relevance = c("Irrelevant", "NonErotic", "Irrelevant"),
                 y =c(0.4, 0.20, 0.40))



pred_a3 |>
  mutate(Gender = fct_relevel(Gender, "Male", "Female"),
         ConditionBelief = fct_recode(ConditionBelief, "Congruent" = "True", "Incongruent" = "False"),
         ConditionBelief = fct_relevel(ConditionBelief, "Congruent", "Incongruent")) |>
  ggplot(aes(x=Relevance, y=Probability)) +
    geom_hline(yintercept=0, color="darkgrey") +
  geom_line(aes(group=Condition, color=Condition), position = position_dodge(width=0.4), alpha=0.8, linewidth=0.2) +
  geom_pointrange(aes(ymin = CI_low, ymax=CI_high, color=Condition), position = position_dodge(width=0.4), size=0.6) +
  geom_text(data=pd, aes(y=y, label = label), hjust=0.5, size = 3.5) +
  geom_text(data=pd_small, aes(y=y, label = label), hjust=0.5, size = 2.5) +

  geom_rect(data=data.frame(Probability=0.1, Gender=as.factor("Male"), ConditionBelief="Congruent", Relevance="Relevant"),
            aes(xmin=0.8, xmax=1.2, ymin=0.45, ymax=0.75), color="#8BC34A", alpha=0, linewidth = 1.2) +
  geom_rect(data=data.frame(Probability=0.1, Gender=as.factor("Female"), ConditionBelief="Congruent", Relevance="Relevant"),
            aes(xmin=0.8, xmax=1.2, ymin=0.20, ymax=0.50), color="#8BC34A", alpha=0, linewidth = 1.2) +
  geom_rect(data=data.frame(Probability=0.1, Gender=as.factor("Male"), ConditionBelief="Incongruent", Relevance="Relevant"),
            aes(xmin=0.8, xmax=1.2, ymin=0.40, ymax=0.7), color="#8BC34A", alpha=0, linewidth = 1.2) +
  geom_rect(data=data.frame(Probability=0.1, Gender=as.factor("Female"), ConditionBelief="Incongruent", Relevance="Relevant"),
            aes(xmin=0.8, xmax=1.2, ymin=0.20, ymax=0.50), color="#8BC34A", alpha=0, linewidth = 1.2) +

    geom_rect(data=data.frame(Probability=0.1, Gender=as.factor("Female"), ConditionBelief="Congruent", Relevance="Irrelevant"),
            aes(xmin=1.8, xmax=2.2, ymin=0.17, ymax=0.45), color="#8BC34A", alpha=0, linewidth = 1.2) +
    geom_rect(data=data.frame(Probability=0.1, Gender=as.factor("Female"), ConditionBelief="Incongruent", Relevance="Irrelevant"),
            aes(xmin=1.8, xmax=2.2, ymin=0.17, ymax=0.45), color="#8BC34A", alpha=0, linewidth = 1.2) +
  facet_grid(Gender~ConditionBelief, switch = "y") +
  geom_rect(data=data.frame(Probability=0.1, Gender=as.factor("Male"), ConditionBelief="Congruent", Relevance="NonErotic"),
            aes(xmin=2.8, xmax=3.2, ymin=0.05, ymax=0.25), color="#8BC34A", alpha=0, linewidth =1.2 ) +
  facet_grid(Gender~ConditionBelief, switch = "y") +
  
  scale_y_continuous(limits=c(0, 0.7), labels=scales::percent) +
  scale_color_manual(values=c("AIGenerated"="#2196F3", "Photograph"="#F44336")) +
  theme_minimal() +
    theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        axis.text.y = element_text(size = 8, face = "bold"),
        strip.placement = "outside",
        strip.background.x = element_rect(fill=c("lightgrey"), color=NA),
        strip.text.x = element_text(size = 12, face = "bold"),
        strip.text.y = element_text(size = 10, face = "bold"),
        axis.text.x = element_text(angle=25, hjust=1, vjust=1.1, size=10, color="black"),
        legend.text = element_text(size = 10),
        legend.position = "bottom") +
  labs(color="Images presented as:")

```

```{r}
#estimate_contrasts(m, contrast = "Condition", by=c("Gender", "Relevance", "ConditionBelief"), comparison = "(b1 - b7) = (b2 - b8)") 

```
:::

### Inter-individual Variability

::: panel-tabset
#### Random effects

<!-- Random effects indicate minimal reliable inter-individual in response to the label manipulation (i.e., individual differences in how AI interacts with relevance are not reliable)  -->

```{r arousal 1 d_vour}

m <- modelbased::estimate_grouplevel(m)
table_dvour(m)
```

#### Participant effects

```{r arousal 1 ppt effects}
#| fig-width: 20
colors <- c(
  "Intercept" = "#9C27B0",                   
  "Irrelevant" = "#1E88E5",   
  "Non-Erotic"  = "#43A047",
  "Relevant:AI-Generated"  = "#E53935",
  "Irrelevant:AI-Generated" = "#00897B",
  "Non-Erotic:AI-Generated" = "#FF9800")

## plot for participant effects
p_dvour <- function(m, colors){
  m |>
    mutate(
      Group = fct_relevel(Group, "Participant", "Item"),
      Parameter = fct_relevel(Parameter, "Intercept", "RelevanceIrrelevant", "RelevanceNonErotic",
"RelevanceRelevant:ConditionAIGenerated",                      "RelevanceIrrelevant:ConditionAIGenerated", "RelevanceNonErotic:ConditionAIGenerated"),
    Parameter = fct_recode(
      Parameter,
      `Non-Erotic:AI-Generated` = "RelevanceNonErotic:ConditionAIGenerated",
      `Relevant:AI-Generated`  = "RelevanceRelevant:ConditionAIGenerated",
      `Irrelevant`            = "RelevanceIrrelevant",
      `Irrelevant:AI-Generated`= "RelevanceIrrelevant:ConditionAIGenerated",
      `Non-Erotic`             = "RelevanceNonErotic"))|>
    ggplot(aes(x = Median , y = Level)) +
    geom_pointrange(
      aes(xmin = CI_low, xmax = CI_high, color = Parameter),
      linewidth = 0.3, size = 0.05
    ) +
    facet_grid(Group ~ Parameter, scales = "free", switch = "both") +
    ggside::ggside(scales = "free") +
    ggside::geom_xsidedensity(aes(fill = Parameter), color = NA) +
    # scale_x_continuous(limits = c(-3, 3), breaks = seq(-3, 3, 1)) +
    scale_color_manual(values = colors) +
    scale_fill_manual(values = colors) +
    theme_minimal() +
   theme(
      axis.text.y = element_blank(),
      axis.ticks.y = element_blank(),
      strip.placement.x = "outside",
      strip.background = element_rect(fill = NA, color = NA),
      axis.title = element_blank(),
      panel.grid.minor = element_blank(),
      panel.grid.major.y = element_blank(),
      axis.text.x = element_text(hjust = 1, size = 12),
      legend.position = "none"
    )
}
```

```{r arousal ppt effect plot}
p_dvour(m, colors)
```

#### Sample analysis

```{r arousal 1 sample df}

m_sample <- m |>
  select(Group, Level, Parameter, Median) |>
  filter(Group == "Participant" & Parameter %in% c("Intercept","RelevanceRelevant:ConditionAIGenerated")) |>
  pivot_wider(names_from = "Parameter", values_from = "Median") |>
  select(!Group) |>
  rename("Participant" = "Level") 
  

df <- dfsub1 |>
  left_join(m_sample, by = "Participant") |>
  rename("Gender" = "Sex") |>
  mutate(
    Region = case_when(
      Country %in% c("Austria", "Belgium", "Czech Republic", "Denmark",
                     "Estonia", "Finland", "France", "Germany", "Greece",
                     "Hungary", "Ireland", "Italy", "Netherlands",
                     "Norway", "Poland", "Portugal", "Romania",
                     "Russia", "Spain", "Sweden", "UK") ~ "Europe",
      Country %in% c("Canada", "USA") ~ "North America",
      Country %in% c("Mexico", "Brazil", "Argentina", "Colombia",
                     "Peru", "Paraguay", "Ecuador") ~ "South America",
      Country %in% c("China", "India", "Indonesia", "Pakistan",
                     "Philippines", "Singapore") ~ "Asia",
      Country %in% c("Australia", "New Zealand") ~ "Oceania",
      Country %in% c("Egypt") ~ "Africa",
      .default = NA))

```

```{r arousal 1 sample analysis}

results_table(lm(`RelevanceRelevant:ConditionAIGenerated` ~ Intercept + Sample, data = df))
```

```{r arousal 1 country analysis}

results_table(lm(`RelevanceRelevant:ConditionAIGenerated` ~ Intercept + Region, data = df))
```
:::

### Correlations (moderators)

<!-- We extracted the random effects and correlated them with other variables in the dataset to look at whether these variables "moderated" the effect of condition. Correlations were overall weak - variability in the intercept and relevance-related parameters was not meaningfully associated with participants’ sexual behaviour or their beliefs and attitudes towards AI.  -->

```{r df 1 corr}

correlations <- df1 |>
  select(Participant, starts_with("BAIT"), starts_with("GAAIS"), starts_with("Porn"), "AI_Knowledge", "SexualActivity_num", "COPS_Frequency_2") |>
  rename(SexualActivity = SexualActivity_num)


corr_mod <- function(m, correlations){
  features1 <- reshape_grouplevel(m, indices = "Median", group = "Participant") |> 
  full_join(correlations, by = "Participant")  |>
  rename(`Non-Erotic:AI-Generated` = `RelevanceNonErotic:ConditionAIGenerated`,
           `Relevant:AI-Generated`= `RelevanceRelevant:ConditionAIGenerated`,
           `Irrelevant` = `RelevanceIrrelevant`,
           `Irrelevant:AI-Generated` = `RelevanceIrrelevant:ConditionAIGenerated`,
           `Non-Erotic` = `RelevanceNonErotic`)
  

  cordata <- correlation::correlation(select(features1, -Participant), p_adjust = "none", redundant = TRUE) |> 
    correlation::cor_sort() |>
    correlation::cor_lower() |>
    as.data.frame() |>
      mutate(Parameter2 = fct_rev(Parameter2),
         Parameter1 = fct_relabel(Parameter1, \(x) gsub("_Intercept", "", x)),
         Parameter2 = fct_relabel(Parameter2, \(x) gsub("_Intercept", "", x)),
         Parameter1 = fct_relabel(Parameter1, \(x) gsub("_", " - ", x)),
         Parameter2 = fct_relabel(Parameter2, \(x) gsub("_", " - ", x)))
  
  p2_cor <- cordata |> 
    ggplot(aes(x=Parameter2, y = Parameter1)) +
    geom_tile(aes(fill = r)) +
    geom_text(aes(label = insight::format_value(r, 2, zap_small = TRUE, lead_zero = FALSE)), color = ifelse(cordata$p < 0.01, "black", "grey")) +
    scale_fill_gradient2(low = "blue", mid = "white", high = "red", midpoint = 0) +
    theme_minimal() +
    theme(
      axis.text.x = element_text(angle = 45, hjust = 1),
      axis.title.x = element_blank(),
      axis.title.y = element_blank(),
      legend.position = "none"
    )
  p2_cor
  
}

```

```{r arousal 1 corr}

corr_mod(m, correlations)

```

## Enticement

```{r enticement 1 by condition belief plot }
df1 |> 
  ggplot(aes(x = Gender, y = Enticement, fill = ConditionBelief)) +
  geom_violin(position = position_dodge(width = 1), alpha = 0.7, trim = FALSE) +
  stat_pointinterval(position = position_dodge(width = 1),point_size = 1.5) +
  facet_grid(Relevance ~ Condition) +
  scale_fill_manual(values = c("True" = "#E66100", "False" = "#5D3A9B")) +
  theme_minimal(base_size = 14) +
  labs(subtitle ="Study 1", x = "Gender",y = "Enticement",fill = "Condition Belief")
```

```{r enticement 1 model load}
#| cache: false
 
m <- readRDS("models/ZOIB/ModelEnticement_1_ZOIB.rds")
```

<!-- Females reported lower enticement than males. Enticement was highest for relevant images with smaller relevance effects among females. Labeling images as AI-generated was associated with reduced enticement. -->

<!-- Participants who maintained label congruency across phases reported higher enticement than those who changed labels; this effect was larger for males. -->

```{r enticement 1 model analysis}
params_table(m)
summary(m, robust = TRUE)
# performance::performance(m)
```

### Marginal Contrasts
::: panel-tabset

#### Effect of Relevance


```{r enticement est cont relevance}
#| message: false
#| warning: false

estimate_contrasts(m, contrast = "Relevance", by="Gender", backend = "emmeans") 

#estimate_contrasts(m, contrast= "Condition", by = c("Gender"),  comparison = "(b1 - b2) = (b3 - b4)")
```

#### Effect of Condition 


```{r enticement est cont condition}
#| message: false
#| warning: false

estimate_contrasts(m, contrast = "Condition", by=c("Gender", "Relevance"), backend = "emmeans") 
```


#### Effect of Condition depending on congruency

<!-- When participants maintained label congruency across phases, photographs were rated as more enticing than AI-generated images, particularly for relevant content, similar to arousal. This pattern reversed for when the labels were incongruent.  -->

```{r enticement est cont}
estimate_contrasts(m, contrast = "Condition", by=c("Gender", "Relevance", "ConditionBelief"), backend = "emmeans")
```

```{r enticement 1 model plot}
#| message: false
#| warning: false

pred_e <- modelbased::estimate_means(m, by=c("Gender", "Relevance", "Condition", "ConditionBelief"), backend = "emmeans") |>
  as.data.frame()

pd <- data.frame(label=c("pd = 100%", "pd = 100%", "pd = 100%", "pd = 100%"),
                 Gender = c("Male", "Female", "Male", "Female"),
                 ConditionBelief = c("Congruent", "Congruent", "Incongruent", "Incongruent"),
                 Relevance = c("Relevant", "Relevant", "Relevant", "Relevant"),
                 y =c(0.80, 0.65, 0.8, 0.65))

pd_small <- data.frame(label=c("pd = 99.89%", "pd = 100%", "pd = 100%", "pd = 98.25%", "pd = 100%", "pd = 97.62%"),
                 Gender = c("Male", "Female", "Male", "Male", "Female", "Female"),
                 ConditionBelief = c("Congruent", "Congruent", "Congruent", "Incongruent", "Incongruent", "Incongruent"),
                 Relevance = c("Irrelevant", "Irrelevant", "NonErotic", "Irrelevant", "Irrelevant", "NonErotic"),
                 y =c(0.45, 0.6, 0.35, 0.45, 0.6, 0.45))



pred_e |>
  mutate(Gender = fct_relevel(Gender, "Male", "Female"),
         ConditionBelief = fct_recode(ConditionBelief, "Congruent" = "True", "Incongruent" = "False"),
         ConditionBelief = fct_relevel(ConditionBelief, "Congruent", "Incongruent")) |>
  ggplot(aes(x=Relevance, y=Probability)) +
    geom_hline(yintercept=0, color="darkgrey") +
  geom_line(aes(group=Condition, color=Condition), position = position_dodge(width=0.4), alpha=0.8, linewidth=0.2) +
  geom_pointrange(aes(ymin = CI_low, ymax=CI_high, color=Condition), position = position_dodge(width=0.4), size=0.2) +
  geom_text(data=pd, aes(y=y, label = label), hjust=0.5, size = 3.5) +
  geom_text(data=pd_small, aes(y=y, label = label), hjust=0.5, size = 2.5) +
  
  geom_rect(data=data.frame(Probability=0.1, Gender=as.factor("Male"), ConditionBelief="Congruent", Relevance="Relevant"),
            aes(xmin=0.8, xmax=1.2, ymin=0.45, ymax=0.75), color="#8BC34A", alpha=0, linewidth = 1.2) +
  geom_rect(data=data.frame(Probability=0.1, Gender=as.factor("Female"), ConditionBelief="Congruent", Relevance="Relevant"),
            aes(xmin=0.8, xmax=1.2, ymin=0.3, ymax=0.60), color="#8BC34A", alpha=0, linewidth = 1.2) +
  geom_rect(data=data.frame(Probability=0.1, Gender=as.factor("Male"), ConditionBelief="Incongruent", Relevance="Relevant"),
            aes(xmin=0.8, xmax=1.2, ymin=0.45, ymax=0.75), color="#8BC34A", alpha=0, linewidth = 1.2) +
  geom_rect(data=data.frame(Probability=0.1, Gender=as.factor("Female"), ConditionBelief="Incongruent", Relevance="Relevant"),
            aes(xmin=0.8, xmax=1.2, ymin=0.30, ymax=0.60), color="#8BC34A", alpha=0, linewidth = 1.2) +
  # 
  #   geom_rect(data=data.frame(Probability=0.1, Gender=as.factor("Female"), ConditionBelief="Congruent", Relevance="Irrelevant"),
  #           aes(xmin=1.8, xmax=2.2, ymin=0.17, ymax=0.45), color="#8BC34A", alpha=0, linewidth = 0.5) +
  # facet_grid(Gender~ConditionBelief, switch = "y") +
  #   geom_rect(data=data.frame(Probability=0.1, Gender=as.factor("Female"), ConditionBelief="Incongruent", Relevance="Irrelevant"),
  #           aes(xmin=1.8, xmax=2.2, ymin=0.17, ymax=0.45), color="#8BC34A", alpha=0, linewidth = 0.5) +
  # facet_grid(Gender~ConditionBelief, switch = "y") +
  # geom_rect(data=data.frame(Probability=0.1, Gender=as.factor("Male"), ConditionBelief="Congruent", Relevance="NonErotic"),
  #           aes(xmin=2.8, xmax=3.2, ymin=0.05, ymax=0.25), color="#8BC34A", alpha=0, linewidth = 0.5) +
  facet_grid(Gender~ConditionBelief, switch = "y") +
  
  scale_y_continuous(limits=c(0, 1), labels=scales::percent) +
  scale_color_manual(values=c("AIGenerated"="#2196F3", "Photograph"="#F44336")) +
  theme_minimal() +
    theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        axis.text.y = element_text(size = 8, face = "bold"),
        strip.placement = "outside",
        strip.background.x = element_rect(fill=c("lightgrey"), color=NA),
        strip.text.x = element_text(size = 10, face = "bold"),
        strip.text.y = element_text(size = 10, face = "bold"),
        axis.text.x = element_text(angle=25, hjust=1, vjust=1.1, size=9, color="black"),
        legend.text = element_text(size = 10),
        legend.position = "bottom") +
  labs(color="Images presented as:")
```
:::

### Inter-individual Variability

::: panel-tabset
#### Random effects

<!-- Random effects indicate minimal reliable inter-individual in response to the label manipulation (i.e., individual differences in how AI interacts with relevance in terms of enticement ratings are not reliable)  -->

```{r enticement 1 d_vour}
m <- modelbased::estimate_grouplevel(m)
table_dvour(m)
```

#### Participant effects

```{r enticement 1 ppt effects}
#| fig-width: 20
p_dvour(m, colors)
```

#### Sample analysis

```{r enticement 1 sample df}

m_sample <- m |>
  select(Group, Level, Parameter, Median) |>
  filter(Group == "Participant" & Parameter %in% c("Intercept","RelevanceRelevant:ConditionAIGenerated")) |>
  pivot_wider(names_from = "Parameter", values_from = "Median") |>
  select(!Group) |>
  rename("Participant" = "Level") 
  

df <- dfsub1 |>
  left_join(m_sample, by = "Participant") |>
  rename("Gender" = "Sex") |>
  mutate(
  Region = case_when(
      Country %in% c("Austria", "Belgium", "Czech Republic", "Denmark",
                     "Estonia", "Finland", "France", "Germany", "Greece",
                     "Hungary", "Ireland", "Italy", "Netherlands",
                     "Norway", "Poland", "Portugal", "Romania",
                     "Russia", "Spain", "Sweden", "UK") ~ "Europe",
      Country %in% c("Canada", "USA") ~ "North America",
      Country %in% c("Mexico", "Brazil", "Argentina", "Colombia",
                     "Peru", "Paraguay", "Ecuador") ~ "South America",
      Country %in% c("China", "India", "Indonesia", "Pakistan",
                     "Philippines", "Singapore") ~ "Asia",
      Country %in% c("Australia", "New Zealand") ~ "Oceania",
      Country %in% c("Egypt") ~ "Africa",
      .default = NA))

```

```{r enticement 1 sample analysis}

results_table(lm(`RelevanceRelevant:ConditionAIGenerated` ~ Intercept + Sample, data = df))
```

```{r enticement 1 country analysis}
results_table(lm(`RelevanceRelevant:ConditionAIGenerated` ~ Intercept + Region, data = df))
```
:::

### Correlations (moderators)

```{r enticement 1 corr}
corr_mod(m, correlations)
```

## Valence
```{r valence 1 by condition belief plot }
df1 |> 
  ggplot(aes(x = Gender, y = Valence, fill = ConditionBelief)) +
  geom_violin(position = position_dodge(width = 1), alpha = 0.7, trim = FALSE) +
  stat_pointinterval(position = position_dodge(width = 1),point_size = 1.5) +
  facet_grid(Relevance ~ Condition) +
  scale_fill_manual(values = c("True" = "#E66100", "False" = "#5D3A9B")) +
  theme_minimal(base_size = 14) +
  labs(subtitle ="Study 1", x = "Gender",y = "Valence",fill = "Condition Belief")
```

```{r valence 1 model}
m <- readRDS("models/ZOIB/ModelValence_1_ZOIB.rds")
```

Females reported lower enticement than males. Enticement was highest for relevant images with smaller relevance effects among females. Labeling images as AI-generated was associated with reduced enticement.

Participants who maintained label congruency across phases reported higher enticement than those who changed labels; this effect was larger for males.

```{r valence 1 model analysis}
params_table(m)
summary(m, robust = TRUE)
# performance::performance(m)
```

### Marginal Contrasts 

::: panel-tabset

#### Effect of Relevance

```{r valence est cont relevance}
#| message: false
#| warning: false

estimate_contrasts(m, contrast = "Relevance", by="Gender", backend = "emmeans") 


```

#### Effect of Condition 

```{r valence est cont condition}
#| message: false
#| warning: false

estimate_contrasts(m, contrast = "Condition", by=c("Gender", "Relevance"), backend = "emmeans") 
```

#### Effect of Condition depending on congruency

```{r valence est cont}
estimate_contrasts(m, contrast = "Condition", by=c("Gender", "Relevance", "ConditionBelief"), backend = "emmeans")
```

```{r valence 1 model pred}
#| message: false
#| warning: false

pred_v <- modelbased::estimate_means(m, by=c("Gender", "Relevance", "Condition", "ConditionBelief"), backend = "emmeans") |>
  as.data.frame()

pd <- data.frame(label=c("pd = 100%", "pd = 100%", "pd = 100%", "pd = 100%"),
                 Gender = c("Male", "Female", "Male", "Female"),
                 ConditionBelief = c("Congruent", "Congruent", "Incongruent", "Incongruent"),
                 Relevance = c("Relevant", "Relevant", "Relevant", "Relevant"),
                 y =c(0.80, 0.65, 0.80, 0.65))

pd_small <- data.frame(label=c("pd = 100%", "pd = 100%", "pd = 100%", "pd = 100%", "pd = 99.99%", "pd = 100%", "pd = 99.63%", "pd = 100%"),
                 Gender = c("Male", "Female", "Male", "Female", "Male", "Female",  "Male", "Female"),
                 ConditionBelief = c("Congruent", "Congruent", "Congruent", "Congruent", "Incongruent", "Incongruent", "Incongruent", "Incongruent"),
                 Relevance = c("Irrelevant", "Irrelevant", "NonErotic", "NonErotic", "Irrelevant", "Irrelevant", "NonErotic", "NonErotic"),
                 y =c(0.5, 0.6, 0.65, 0.7, 0.5, 0.6, 0.65, 0.65))



pred_v |>
  mutate(Gender = fct_relevel(Gender, "Male", "Female"),
         ConditionBelief = fct_recode(ConditionBelief, "Congruent" = "True", "Incongruent" = "False"),
         ConditionBelief = fct_relevel(ConditionBelief, "Congruent", "Incongruent")) |>
  ggplot(aes(x=Relevance, y=Probability)) +
    geom_hline(yintercept=0, color="darkgrey") +
  geom_line(aes(group=Condition, color=Condition), position = position_dodge(width=0.4), alpha=0.8, linewidth=0.2) +
  geom_pointrange(aes(ymin = CI_low, ymax=CI_high, color=Condition), position = position_dodge(width=0.4), size=0.2) +
  geom_text(data=pd, aes(y=y, label = label), hjust=0.5, size = 3.5) +
  geom_text(data=pd_small, aes(y=y, label = label), hjust=0.5, size = 2.5) +
  
  geom_rect(data=data.frame(Probability=0.1, Gender=as.factor("Male"), ConditionBelief="Congruent", Relevance="Relevant"),
            aes(xmin=0.8, xmax=1.2, ymin=0.45, ymax=0.75), color="#8BC34A", alpha=0, linewidth = 1.2) +
  geom_rect(data=data.frame(Probability=0.1, Gender=as.factor("Female"), ConditionBelief="Congruent", Relevance="Relevant"),
            aes(xmin=0.8, xmax=1.2, ymin=0.35, ymax=0.6), color="#8BC34A", alpha=0, linewidth = 1.2) +
  geom_rect(data=data.frame(Probability=0.1, Gender=as.factor("Male"), ConditionBelief="Incongruent", Relevance="Relevant"),
            aes(xmin=0.8, xmax=1.2, ymin=0.45, ymax=0.75), color="#8BC34A", alpha=0, linewidth = 1.2) +
  geom_rect(data=data.frame(Probability=0.1, Gender=as.factor("Female"), ConditionBelief="Incongruent", Relevance="Relevant"),
            aes(xmin=0.8, xmax=1.2, ymin=0.30, ymax=0.6), color="#8BC34A", alpha=0, linewidth = 1.2) +
  # 
  #   geom_rect(data=data.frame(Probability=0.1, Gender=as.factor("Female"), ConditionBelief="Congruent", Relevance="Irrelevant"),
  #           aes(xmin=1.8, xmax=2.2, ymin=0.17, ymax=0.45), color="#8BC34A", alpha=0, linewidth = 0.5) +
  # facet_grid(Gender~ConditionBelief, switch = "y") +
  #   geom_rect(data=data.frame(Probability=0.1, Gender=as.factor("Female"), ConditionBelief="Incongruent", Relevance="Irrelevant"),
  #           aes(xmin=1.8, xmax=2.2, ymin=0.17, ymax=0.45), color="#8BC34A", alpha=0, linewidth = 0.5) +
  # facet_grid(Gender~ConditionBelief, switch = "y") +
  # geom_rect(data=data.frame(Probability=0.1, Gender=as.factor("Male"), ConditionBelief="Congruent", Relevance="NonErotic"),
  #           aes(xmin=2.8, xmax=3.2, ymin=0.05, ymax=0.25), color="#8BC34A", alpha=0, linewidth = 0.5) +
  facet_grid(Gender~ConditionBelief, switch = "y") +
  
  scale_y_continuous(limits=c(0, 1), labels=scales::percent) +
  scale_color_manual(values=c("AIGenerated"="#2196F3", "Photograph"="#F44336")) +
  theme_minimal() +
    theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        axis.text.y = element_text(size = 8, face = "bold"),
        strip.placement = "outside",
        strip.background.x = element_rect(fill=c("lightgrey"), color=NA),
        strip.text.x = element_text(size = 10, face = "bold"),
        strip.text.y = element_text(size = 10, face = "bold"),
        axis.text.x = element_text(angle=25, hjust=1, vjust=1.1, size=9, color="black"),
        legend.text = element_text(size = 10),
        legend.position = "bottom") +
  labs(color="Images presented as:")
```
:::

### Inter-individual Variability

::: panel-tabset
#### Random effects

```{r valence 1 d_vour}

m <- modelbased::estimate_grouplevel(m)
table_dvour(m)
```

#### Participant effects

```{r valence 1 ppt effects}
#| fig-width: 20

p_dvour(m, colors)
```

#### Sample analysis


```{r valence 1 sample df}

m_sample <- m |>
  select(Group, Level, Parameter, Median) |>
  filter(Group == "Participant" & Parameter %in% c("Intercept","RelevanceRelevant:ConditionAIGenerated")) |>
  pivot_wider(names_from = "Parameter", values_from = "Median") |>
  select(!Group) |>
  rename("Participant" = "Level") 
  

df <- dfsub1 |>
  left_join(m_sample, by = "Participant") |>
  rename("Gender" = "Sex") |>
  mutate(
    Region = case_when(
      Country %in% c("Austria", "Belgium", "Czech Republic", "Denmark",
                     "Estonia", "Finland", "France", "Germany", "Greece",
                     "Hungary", "Ireland", "Italy", "Netherlands",
                     "Norway", "Poland", "Portugal", "Romania",
                     "Russia", "Spain", "Sweden", "UK") ~ "Europe",
      Country %in% c("Canada", "USA") ~ "North America",
      Country %in% c("Mexico", "Brazil", "Argentina", "Colombia",
                     "Peru", "Paraguay", "Ecuador") ~ "South America",
      Country %in% c("China", "India", "Indonesia", "Pakistan",
                     "Philippines", "Singapore") ~ "Asia",
      Country %in% c("Australia", "New Zealand") ~ "Oceania",
      Country %in% c("Egypt") ~ "Africa",
      .default = NA))

```

```{r valence 1 sample analysis}

results_table(lm(`RelevanceRelevant:ConditionAIGenerated` ~ Intercept + Sample, data = df))
```

```{r valence 1 country analysis}
results_table(lm(`RelevanceRelevant:ConditionAIGenerated` ~ Intercept + Region, data = df))
```
:::

### Correlations (moderators)

```{r valence 1 corr}
corr_mod(m, correlations)
```
:::


# Figures
