---
title: "FictionEro2 - Affective Impact of Fiction"
editor: source
editor_options: 
  chunk_output_type: console
format:
  html:
    code-fold: true
    self-contained: false
    toc: true
---

## Data Preparation

```{r}
#| message: false
#| warning: false

library(tidyverse)
library(easystats)
library(patchwork)
library(ggside)
library(glmmTMB)

options(mc.cores = parallel::detectCores(),
        brms.backend = "cmdstanr",
        width = 300)
```

**notes**: How about confidence on all AI and all photos.

```{r}
dfsub <- read.csv("../data/data_participants.csv")
df <- read.csv("../data/data.csv") |> 
  right_join(
    select(dfsub, Participant, Mobile, starts_with(c("Feedback_","BAIT")), COPS_Frequency_2, GenderualActivity,
           -Feedback_Text),
    by = "Participant"
    ) |> 
  mutate(Condition = fct_relevel(Condition, "Reality", "Fiction"),
         Gender =  fct_relevel(Gender, "Male", "Female", "Other"),
         PornFrequency = as.numeric(as.factor(COPS_Frequency_2)),
         GenderualActivity_num = as.numeric(as.factor(GenderualActivity)),
         ConditionBelief = case_when(
           Condition == "Reality" & Realness > 0.5 ~ "True",
           Condition == "AI-Fiction" & Realness < 0.5 ~ "True",
           .default = "False",
         )) |> 
  mutate(Condition = case_when(
    Condition == "Fiction" ~ "AI-Generated",
    Condition == "Reality" ~ "Photograph"
  )) |>
  mutate(across(starts_with("Feedback_")& !matches("Feedback_AllRealConfidence|Feedback_AllFakeConfidence|Feedback_Enjoyment"), function(x) {fct_relevel(x, "False", "True")}))

results_table <- function(model, effects="fixed", filter=NULL) {
  if("marginaleffects" %in% class(model)) {
    model |> 
      parameters::parameters() |> 
      as.data.frame() |> 
      select(-Parameter, -SE, -S, z=Statistic, -Predicted) |> 
      insight::format_table() |> 
      parameters::display()
  } else {
    display(parameters::parameters(model, effects=effects, keep=filter))
  }
}
```

## Manipulation Check

This section is about selecting the best model. Notably, all the stimuli presented are of an erotic nature.

**Note to dom** beta model does not make sense anymore, what else should we do?

::: panel-tabset

### Arousal

```{r}
arousal <- df |> 
  ggplot(aes(x=Arousal)) +
  geom_histogram(fill="grey", position = "identity", binwidth = 0.5) +
  scale_y_sqrt(expand = c(0, 0)) +
  scale_x_continuous(breaks = (0:6), labels = c("Not at all", "1", "2", "3", "4", "5", "Very much")) +
  labs(title = "Arousal") +
  theme_abyss() +
  theme(plot.title = element_text(hjust = 0.5, face="bold"))

arousal
```

```{r}

df |> 
  mutate(ConditionBelief = as.factor(ConditionBelief)) |> 
  mutate(ConditionBelief = case_when(
    ConditionBelief == "False" ~ "Not Believed",
    ConditionBelief == "True" ~ "Believed",)) |>
  ggplot(aes(x=Arousal, fill=Gender)) +
  geom_histogram(position = "identity", binwidth = 0.5) +
  facet_grid(Gender~ConditionBelief, scales="free_y") +
  scale_color_manual(values=c("red", "white"), guide="none") +
  scale_fill_manual(values=c("Female"="#E91E63", "Male"="#FF9800", "Other" = "#03A9F4"), guide="none") +
  # scale_y_sqrt(expand = c(0, 0)) +
  labs(title = "Arousal to images believed or not to be AI-Gnerated") +
  theme_abyss() +
  theme(plot.title = element_text(hjust = 0.5, face="bold"))
```

**Note**:  Model m3, which includes random intercepts and random slopes for Gender at the stimulus level, exhibits relatively high correlations between the random intercepts and slopes. This suggests that the random effects are strongly correlated, which could indicate overfitting.

```{r}
#| eval: false

# Get a sense of Random Factors
m1 <- glmmTMB::glmmTMB(Arousal ~ Gender + (1|Participant), data=df)
m2 <- glmmTMB::glmmTMB(Arousal ~ Gender + (1|Participant) + (1|Stimulus ), data=df)
m3 <- glmmTMB::glmmTMB(Arousal ~ Gender + (1|Participant) + (1+Gender|Stimulus ), data=df)


test_bf(m1,m2)
compare_performance(m1, m2)

# the model with participants and stimuli as random effecs seems to be the best
```

This model evaluate ths the effects of Gender on Arousal, accounting for random variability due to participants and the stimuli (i.e., random effects). 

The analysis revealed that on average **women rate erotic stimuli significantly lower in arousal than men**, while participants identifying as 'other' rate on average erotic stimuli higher than men, however this is not significant.

```{r}
m_a <- glmmTMB::glmmTMB(Arousal ~ Gender + (1|Participant) + (1|Stimulus ),
                      data=df,
                      control = glmmTMB::glmmTMBControl(parallel = 8))
                      # control = glmmTMB::glmmTMBControl(optimizer=stats::optim, # nlminb, optim
                      #                                   optArgs = list(method = "BFGS"),  #Nelder-Mead, BFGS, CG
                      #                                   parallel = 8))

results_table(m_a)

```

```{r}
estimate_relation(m_a) |> 
  ggplot(aes(x=Gender, y=Predicted)) +
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high, color = Gender), position=position_dodge(width=0.5)) +
 scale_color_manual(values=c("Male"="#E91E63", "Female"="#FF9800","Other"="#03A9F4"), guide="none") +  labs(y="Arousal") +
  theme_abyss()
```

### Enticement

```{r}
valence <- df |> 
  ggplot(aes(x=Enticing)) +
  geom_histogram(fill="grey", position = "identity", binwidth = 0.5) +
  scale_y_sqrt(expand = c(0, 0)) +
  scale_x_continuous(breaks = (0:6), labels = c("Not at all", "1", "2", "3", "4", "5", "Very much")) +
  labs(title = "Valence") +
  theme_abyss() +
  theme(plot.title = element_text(hjust = 0.5, face="bold"),
        legend.position = "none")

valence
```

```{r}

df |> 
  mutate(ConditionBelief = as.factor(ConditionBelief)) |> 
  mutate(ConditionBelief = case_when(
    ConditionBelief == "False" ~ "Not Believed",
    ConditionBelief == "True" ~ "Believed",)) |>
  ggplot(aes(x=Enticing, fill=Gender)) +
  geom_histogram(position = "identity", binwidth = 0.5) +
  facet_grid(Gender~ConditionBelief, scales="free_y") +
  scale_color_manual(values=c("red", "white"), guide="none") +
  scale_fill_manual(values=c("Female"="#E91E63", "Male"="#FF9800", "Other" = "#03A9F4"), guide="none") +
  # scale_y_sqrt(expand = c(0, 0)) +
  labs(title = "Enticiment to images believed or not to be AI-Gnerated") +
  theme_abyss() +
  theme(plot.title = element_text(hjust = 0.5, face="bold"))
```

This model evaluate ths the effects of Gender on Enticement, accounting for random variability due to participants and the stimuli (i.e., random effects). Notably, all the stimuli is erotic. 

The analysis revealed that on average **women rate erotic stimuli significantly lower in enticiment than men**, while participants identifying as 'other' rate on average erotic stimuli higher than men. However, these differences were not statistically significant.

```{r}
m_e <- glmmTMB::glmmTMB(Enticing ~ Gender + (1|Participant) + (1|Stimulus ),
                      data=df,
                      control = glmmTMB::glmmTMBControl(parallel = 8))
                      # control = glmmTMB::glmmTMBControl(optimizer=stats::optim, # nlminb, optim
                      #                                   optArgs = list(method = "BFGS"),  #Nelder-Mead, BFGS, CG
                      #                                   parallel = 8))

results_table(m_e)

```

```{r}
estimate_relation(m_e) |> 
  ggplot(aes(x=Gender, y=Predicted)) +
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high, color = Gender), position=position_dodge(width=0.5)) +
 scale_color_manual(values=c("Male"="#E91E63", "Female"="#FF9800","Other"="#03A9F4"), guide="none") +  labs(y="Arousal") +
  theme_abyss()
```


### Valence

```{r}
valence <- df |> 
  ggplot(aes(x=Valence)) +
  geom_histogram(fill="grey", position = "identity", binwidth = 0.5) +
  scale_y_sqrt(expand = c(0, 0)) +
  scale_x_continuous(breaks = (0:6), labels = c("Unpleasant", "1", "2", "3", "4", "5", "Pleasant")) +
  labs(title = "Valence") +
  theme_abyss() +
  theme(plot.title = element_text(hjust = 0.5, face="bold"),
        legend.position = "none")

valence
```

```{r}

df |> 
  mutate(ConditionBelief = as.factor(ConditionBelief)) |> 
  mutate(ConditionBelief = case_when(
    ConditionBelief == "False" ~ "Not Believed",
    ConditionBelief == "True" ~ "Believed",)) |>
  ggplot(aes(x=Valence, fill=Gender)) +
  geom_histogram(position = "identity", binwidth = 0.5) +
  facet_grid(Gender~ConditionBelief, scales="free_y") +
  scale_color_manual(values=c("red", "white"), guide="none") +
  scale_fill_manual(values=c("Female"="#E91E63", "Male"="#FF9800", "Other" = "#03A9F4"), guide="none") +
  # scale_y_sqrt(expand = c(0, 0)) +
  labs(title = "Valence to images believed or not to be AI-Gnerated") +
  theme_abyss() +
  theme(plot.title = element_text(hjust = 0.5, face="bold"))
```


This model evaluate ths the effects of Gender on valence, accounting for random variability due to participants and the stimuli (i.e., random effects). Notably, all the stimuli is erotic. 

<!-- Key Findings -->

The analysis revealed that on average **women rate erotic stimuli significantly lower in arousal than men**, while participants identifying as 'other' rate on average erotic stimuli higher than men,. None of these differences were statistically significant.

```{r}
m_v <- glmmTMB::glmmTMB(Valence ~ Gender + (1|Participant) + (1|Stimulus ),
                      data=df,
                      control = glmmTMB::glmmTMBControl(parallel = 8))
                      # control = glmmTMB::glmmTMBControl(optimizer=stats::optim, # nlminb, optim
                      #                                   optArgs = list(method = "BFGS"),  #Nelder-Mead, BFGS, CG
                      #                                   parallel = 8))

results_table(m_v)

```

```{r}
estimate_relation(m_e) |> 
  ggplot(aes(x=Gender, y=Predicted)) +
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high, color = Gender), position=position_dodge(width=0.5)) +
 scale_color_manual(values=c("Male"="#E91E63", "Female"="#FF9800","Other"="#03A9F4"), guide="none") +  labs(y="Arousal") +
  theme_abyss()
```

:::

## Arousal 

```{r}
#| fig-height: 12
#| fig-width: 7


plot_descriptive <- function(df, target="Arousal") {
  # By item
  order <- df |>
    mutate(.Item_Order = paste0(Gender, "_", Stimulus)) |>
    summarize(mean = mean(.data[[target]], na.rm=TRUE), .by=c("Condition", ".Item_Order")) |> 
    arrange(.Item_Order, desc(Condition)) |> 
    mutate(diff = sign(mean - lag(mean)),
           Relevance = str_extract(.Item_Order, "^[^_]+"),
           .Item_Order = str_extract(.Item_Order, "(?<=_).+")) |>
    filter(Condition == "Photograph") |> 
    arrange(Relevance, diff, mean)
    
  p1 <- df |>
    mutate(.Item_Order = paste0(Gender, "_", Stimulus)) |>
    group_by(.Item_Order, Condition) |>
    ggdist::mean_qi(.data[[target]], .width=0.95) |>
    mutate(Gender = fct_rev(str_extract(.Item_Order, "^[^_]+"))) |>
    left_join(order[c(".Item_Order", "diff")], by=".Item_Order") |>
    mutate(.Item_Order = fct_relevel(.Item_Order, order$.Item_Order)) |>
    # mutate(.average = mean(.data[[target]]), .by="Item") |>
    # mutate(Item = fct_reorder(Item, .average)) |>
    ggplot(aes(y = .Item_Order, x=.data[[target]])) +
    geom_line(aes(color=as.factor(diff)), linewidth=1) +
    geom_point(aes(color=Condition), size=2) +
      
    # ggdist::stat_slabinterval(aes(fill=Condition, color=Condition),
    #                           .width=0.95, normalize="xy", slab_alpha=0.5) +
    # ggdist::stat_histinterval(aes(fill=Condition, color=Condition),
    #                           .width=0.95, normalize="xy", slab_alpha=0.5) +
    scale_color_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336", "1"="#F44336", "-1"="#2196F3"),
                       breaks = c('AI-Generated', 'Photograph')) +
    # scale_fill_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336")) +
    scale_y_discrete(labels = function(x) str_extract(x, "(?<=_).+")) +
    theme_minimal() +
    theme(panel.grid.minor.x = element_blank(),
          # panel.grid.major.x = element_blank(),
          panel.border = element_blank(),
          axis.line.x = element_blank()) +
    labs(title = paste0(target, " by Item"), color="Condition", y="Items") +
    facet_wrap(~Gender, scales="free_y")

  # By participant
  p2 <- df |>
    summarize(.average = mean(.data[[target]]),
              .by=c("Gender", "Participant", "Condition")) |>
    pivot_wider(names_from = Condition, values_from = .average) |>
    mutate(.diff = Photograph - `AI-Generated`) |>
    mutate(Participant = fct_reorder(Participant, .diff)) |>
    ggplot(aes(x = .diff, y=Participant)) +
    geom_bar(aes(fill=.diff), stat = "identity")  +
    scale_fill_gradient2(guide="none", low="red", high="red", mid="blue") +
    labs(title = paste0(target, " by Participant")) +
    facet_wrap(~Gender, ncol=2, scales="free_y") +
    theme_minimal() +
    theme(panel.grid.major.y = element_blank(),
          panel.border = element_blank(),
          axis.line.x = element_blank(),
          axis.text.y = element_blank()) +
    labs(title = paste0(target, " by Participant"), x="Difference (Photograph - AI-Generated)", y="Participants")

  p1 / p2 + plot_layout(heights = c(2, 1))
}

# remove other 
arousal_desc <- df |> 
  filter(Gender != "Other") |> 
  plot_descriptive("Arousal")

arousal_desc
```

### Whole Sample


```{r}

```