---
title: "FictionEro2 - Affective Impact of Fiction"
editor: source
editor_options: 
  chunk_output_type: console
format:
  html:
    code-fold: true
    self-contained: false
    toc: true
---

## Data Preparation

```{r}
#| message: false
#| warning: false

library(tidyverse)
library(easystats)
library(patchwork)
library(ggside)
library(glmmTMB)

options(mc.cores = parallel::detectCores(),
        brms.backend = "cmdstanr",
        width = 300)
```

**notes**: How about confidence on all AI and all photos.

```{r}
#| warning: false
#| 
dfsub <- read.csv("../data/data_participants.csv")

df <- read.csv("../data/data.csv") |> 
  right_join(
    select(dfsub, Participant, Mobile, starts_with(c("Feedback_","BAIT")), COPS_Frequency, SexualActivity,- Feedback_Text),
    by = "Participant"
    ) |> 
  mutate(Condition = case_when(
    Condition == "Fiction" ~ "AI-Generated",
    Condition == "Reality" ~ "Photograph"
  )) |>
  mutate(Condition = fct_relevel(Condition, "Photograph", "AI-Generated"),
         Gender =  fct_relevel(Gender, "Male", "Female"),
         PornFrequency = as.numeric(as.factor(COPS_Frequency)),
         SexurualActivity_num = as.numeric(as.factor(SexualActivity)),
         ConditionBelief = case_when(
           Condition == "Photograph" & Realness > 0 ~ "True",
           Condition == "AI-Generated" & Realness < 0 ~ "True",
           .default = "False",
         )) |>
  rename(AllRealConfidence = "Feedback_AllRealConfidence",
         AllFakeConfidence = "Feedback_AllFakeConfidence",
         Enjoyment = "Feedback_Enjoyment"
         )|>
  mutate(across(starts_with("Feedback_"), as.factor))

results_table <- function(model, effects="fixed", filter=NULL) {
  if("marginaleffects" %in% class(model)) {
    model |> 
      parameters::parameters() |> 
      as.data.frame() |> 
      select(-Parameter, -SE, -S, z=Statistic, -Predicted) |> 
      insight::format_table() |> 
      parameters::display()
  } else {
    display(parameters::parameters(model, effects=effects, keep=filter))
  }
}

## re-scaled variables
scale_values <- function(x){(x-min(x))/(max(x)-min(x))}


df$Arousal <- scale_values(df$Arousal)
df$Enticing <- scale_values(df$Enticing)
df$Valence <- scale_values(df$Valence)
```

**Note**: [These calculations are based on the validation of the BAIT scale](https://realitybending.github.io/FictionEro/study1/analysis/1_cleaning.html)

```{r}

df$BAIT_Videos <- (df$BAIT_VideosRealistic + (1 - df$BAIT_VideosIssues)) / 2

df$BAIT_Visual = (df$BAIT_ImagesRealistic + (1 - df$BAIT_ImagesIssues) + df$BAIT_ImitatingReality + df$BAIT_EnvironmentReal) / 4

df$BAIT_Text = (df$BAIT_TextRealistic + (1 - df$BAIT_TextIssues)) / 2

df$BAIT_Negative <- (df$BAIT_Worry + df$BAIT_Dangerous)/2

df$BAIT_Positive <- (df$BAIT_Exciting + df$BAIT_Benefit)/2
```


## Manipulation Check

This section is about selecting the best model. Notably, all the stimuli presented are of an erotic nature.
Note that variables were rescaled to [0,1] when fitting the models and that the stimuli presented to participants was assigned according to their self-rated sexuality, making all stimuli relevant to participants. 

To summarise, women rate stimuli on average significantly lower in arousal, enticiment and valence than men. 

::: panel-tabset

### Arousal

Arousal ratings were relatively well-distributed across the scale, with the highest frequency for "Not at all" and a gradual decrease across higher ratings. 

The pattern of arousal ratings was similar regardless of whether participants believed the images were AI-generated or real. Among male participants, arousal ratings were relatively evenly distributed but tended to cluster around the middle of the scale, independent of their belief about the images' origin. Female participants, on the other hand, showed a pronounced peak at the lowest arousal rating, irrespective of their perception of the images as AI-generated. Participants with other gender identities provided fewer responses overall, but their arousal ratings generally leaned toward moderate levels, particularly in the "Not Believed" condition.

```{r}
arousal <- df |> 
  ggplot(aes(x=Arousal)) +
  geom_bar(fill="#03A9F4") +
  scale_y_sqrt(expand = c(0, 0)) +
  labs(title = "Arousal", ) +
  theme_abyss() +
  theme(plot.title = element_text(hjust = 0.5, face="bold"))

arousal
```

```{r}

df |> 
  mutate(ConditionBelief = as.factor(ConditionBelief)) |> 
  mutate(ConditionBelief = case_when(
    ConditionBelief == "False" ~ "Not Believed",
    ConditionBelief == "True" ~ "Believed",)) |>
  ggplot(aes(x=Arousal, fill=Gender)) +
  geom_bar(position = "identity") +
  facet_grid(Gender~ConditionBelief, scales="free_y") +
  scale_color_manual(values=c("red", "white"), guide="none") +
  scale_fill_manual(values=c("Female"="#E91E63", "Male"="#FF9800"), guide="none") +
  # scale_y_sqrt(expand = c(0, 0)) +
  labs(title = "Arousal to images believed or not to be AI-Gnerated") +
  theme_abyss() +
  theme(plot.title = element_text(hjust = 0.5, face="bold"))
```

**Note**:  Model m3, which includes random intercepts and random slopes for Gender at the stimulus level, exhibits relatively high correlations between the random intercepts and slopes. This suggests that the random effects are strongly correlated, which could indicate overfitting.

```{r}
#| eval: false

# Get a sense of Random Factors
m1 <- glmmTMB::glmmTMB(Arousal ~ Gender + (1|Participant), data=df)
m2 <- glmmTMB::glmmTMB(Arousal ~ Gender + (1|Participant) + (1|Stimulus ), data=df)
m3 <- glmmTMB::glmmTMB(Arousal ~ Gender + (1|Participant) + (1+Gender|Stimulus ), data=df)


test_bf(m1,m2, m3)
compare_performance(m1, m2)

# the model with participants only as random effecs seems to be the best
```

This model evaluate ths the effects of Gender on Arousal, accounting for random variability due to participants (i.e., random effects). The analysis revealed that on average **women rate erotic stimuli significantly lower in arousal than men**. 

```{r}

m_a <- glmmTMB::glmmTMB(Arousal ~ Gender + (1|Participant),
                      data=df, family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))
                      # control = glmmTMB::glmmTMBControl(optimizer=stats::optim, # nlminb, optim
                      #                                   optArgs = list(method = "BFGS"),  #Nelder-Mead, BFGS, CG
                      #                                   parallel = 8))

results_table(m_a)

```

```{r}
estimate_relation(m_a) |> 
  ggplot(aes(x=Gender, y=Predicted)) +
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high, color = Gender), position=position_dodge(width=0.5)) +
 scale_color_manual(values=c("Male"="#E91E63", "Female"="#FF9800"), guide="none") +  labs(y="Arousal") +
  theme_abyss()
```

### Enticement

Enticement ratings were relatively well-distributed across the scale.

Male participants predominantly provided responses in the mid-to-high enticement range across both conditions. Female participants showed a pronounced peak at the lowest enticement rating when they did not believe the image was AI-generated, with a similar but less pronounced pattern in the believed condition. Participants identifying as 'Other' responses were more concentrated around the middle of the scale.

```{r}
enticiment <- df |> 
  ggplot(aes(x=Enticing)) +
  geom_bar(fill="#03A9F4") +
  scale_y_sqrt(expand = c(0, 0)) +
  labs(title = "Enticement", ) +
  theme_abyss() +
  theme(plot.title = element_text(hjust = 0.5, face="bold"))


enticiment
```

```{r}

df |> 
  mutate(ConditionBelief = as.factor(ConditionBelief)) |> 
  mutate(ConditionBelief = case_when(
    ConditionBelief == "False" ~ "Not Believed",
    ConditionBelief == "True" ~ "Believed",)) |>
  ggplot(aes(x=Enticing, fill=Gender)) +
  geom_bar(position = "identity", binwidth = 0.5) +
  facet_grid(Gender~ConditionBelief, scales="free_y") +
  scale_color_manual(values=c("red", "white"), guide="none") +
  scale_fill_manual(values=c("Female"="#E91E63", "Male"="#FF9800"), guide="none") +
  # scale_y_sqrt(expand = c(0, 0)) +
  labs(title = "Enticiment to images believed or not to be AI-Gnerated") +
  theme_abyss() +
  theme(plot.title = element_text(hjust = 0.5, face="bold"))
```

This model evaluate ths the effects of Gender on Enticement, accounting for random variability due to participants and the stimuli (i.e., random effects). Notably, all the stimuli is erotic. 

The analysis revealed that on average **women rate erotic stimuli significantly lower in enticiment than men**. 

```{r}
m_e <- glmmTMB::glmmTMB(Enticing ~ Gender + (1|Participant),
                      data=df,family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))
                      # control = glmmTMB::glmmTMBControl(optimizer=stats::optim, # nlminb, optim
                      #                                   optArgs = list(method = "BFGS"),  #Nelder-Mead, BFGS, CG
                      #                                   parallel = 8))

results_table(m_e)

```

```{r}
estimate_relation(m_e) |> 
  ggplot(aes(x=Gender, y=Predicted)) +
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high, color = Gender), position=position_dodge(width=0.5)) +
 scale_color_manual(values=c("Male"="#E91E63", "Female"="#FF9800"), guide="none") +  labs(y="Arousal") +
  theme_abyss()
```


### Valence

Valence ratings were concetrated more around the mid-to-high valence. 

Participants showed the same pattern of results regardless of whether they believed the images to be Ai-generated or not. 
Males tended to to have the majority of their responses concentrated in the mid-to-high valence range. Female majoity valence ratings were on on the lower (0) and midle end of the scale (3/4). 

```{r}
valence <- df |> 
  ggplot(aes(x=Valence)) +
  geom_bar(fill="#03A9F4") +
  scale_y_sqrt(expand = c(0, 0)) +
  labs(title = "Valence", ) +
  theme_abyss() +
  theme(plot.title = element_text(hjust = 0.5, face="bold"))

valence
```

```{r}

df |> 
  mutate(ConditionBelief = as.factor(ConditionBelief)) |> 
  mutate(ConditionBelief = case_when(
    ConditionBelief == "False" ~ "Not Believed",
    ConditionBelief == "True" ~ "Believed",)) |>
  ggplot(aes(x=Valence, fill=Gender)) +
  geom_bar(position = "identity", binwidth = 0.5) +
  facet_grid(Gender~ConditionBelief, scales="free_y") +
  scale_color_manual(values=c("red", "white"), guide="none") +
  scale_fill_manual(values=c("Female"="#E91E63", "Male"="#FF9800"), guide="none") +
  # scale_y_sqrt(expand = c(0, 0)) +
  labs(title = "Valence to images believed or not to be AI-Gnerated") +
  theme_abyss() +
  theme(plot.title = element_text(hjust = 0.5, face="bold"))
```


This model evaluate ths the effects of Gender on valence, accounting for random variability due to participants and the stimuli (i.e., random effects). Notably, all the stimuli is erotic. 

<!-- Key Findings -->

The analysis revealed that on average **women rate erotic stimuli significantly lower in valence than men**. 

```{r}
m_v <- glmmTMB::glmmTMB(Valence ~ Gender + (1|Participant), family=glmmTMB::ordbeta(),
                      data=df,
                      control = glmmTMB::glmmTMBControl(parallel = 8))
                      # control = glmmTMB::glmmTMBControl(optimizer=stats::optim, # nlminb, optim
                      #                                   optArgs = list(method = "BFGS"),  #Nelder-Mead, BFGS, CG
                      #                                   parallel = 8))

results_table(m_v)

```

```{r}
estimate_relation(m_v) |> 
  ggplot(aes(x=Gender, y=Predicted)) +
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high, color = Gender), position=position_dodge(width=0.5)) +
 scale_color_manual(values=c("Male"="#E91E63", "Female"="#FF9800"), guide="none") +  labs(y="Arousal") +
  theme_abyss()
```

:::

## Arousal 

In contrast to [study1](https://realitybending.github.io/FictionEro/study1/analysis/2_emotions.html) arousal ratings differ by whether the images were preceeded by 'photograph' or by 'ai-generated'. 


```{r}
#| fig-height: 12
#| fig-width: 7


plot_descriptive <- function(df, target="Arousal") {
  # By item
  order <- df |>
    mutate(.Item_Order = paste0(Gender, "_", Stimulus)) |>
    summarize(mean = mean(.data[[target]], na.rm=TRUE), .by=c("Condition", ".Item_Order")) |> 
    arrange(.Item_Order, desc(Condition)) |> 
    mutate(diff = sign(mean - lag(mean)),
           Relevance = str_extract(.Item_Order, "^[^_]+"),
           .Item_Order = str_extract(.Item_Order, "(?<=_).+")) |>
    filter(Condition == "Photograph") |> 
    arrange(Relevance, diff, mean)
    
  p1 <- df |>
    mutate(.Item_Order = paste0(Gender, "_", Stimulus)) |>
    group_by(.Item_Order, Condition) |>
    ggdist::mean_qi(.data[[target]], .width=0.95) |>
    mutate(Gender = fct_rev(str_extract(.Item_Order, "^[^_]+"))) |>
    left_join(order[c(".Item_Order", "diff")], by=".Item_Order") |>
    mutate(.Item_Order = fct_relevel(.Item_Order, order$.Item_Order)) |>
    # mutate(.average = mean(.data[[target]]), .by="Item") |>
    # mutate(Item = fct_reorder(Item, .average)) |>
    ggplot(aes(y = .Item_Order, x=.data[[target]])) +
    geom_line(aes(color=as.factor(diff)), linewidth=1) +
    geom_point(aes(color=Condition), size=2) +
      
    # ggdist::stat_slabinterval(aes(fill=Condition, color=Condition),
    #                           .width=0.95, normalize="xy", slab_alpha=0.5) +
    # ggdist::stat_histinterval(aes(fill=Condition, color=Condition),
    #                           .width=0.95, normalize="xy", slab_alpha=0.5) +
    scale_color_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336", "1"="#F44336", "-1"="#2196F3"),
                       breaks = c('AI-Generated', 'Photograph')) +
    # scale_fill_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336")) +
    scale_y_discrete(labels = function(x) str_extract(x, "(?<=_).+")) +
    theme_minimal() +
    theme(panel.grid.minor.x = element_blank(),
          # panel.grid.major.x = element_blank(),
          panel.border = element_blank(),
          axis.line.x = element_blank()) +
    labs(title = paste0(target, " by Item"), color="Condition", y="Items") +
    facet_wrap(~Gender, scales="free_y")

  # By participant
  p2 <- df |>
    summarize(.average = mean(.data[[target]]),
              .by=c("Gender", "Participant", "Condition")) |>
    pivot_wider(names_from = Condition, values_from = .average) |>
    mutate(.diff = Photograph - `AI-Generated`) |>
    mutate(Participant = fct_reorder(Participant, .diff)) |>
    ggplot(aes(x = .diff, y=Participant)) +
    geom_bar(aes(fill=.diff), stat = "identity")  +
    scale_fill_gradient2(guide="none", low="red", high="red", mid="blue") +
    labs(title = paste0(target, " by Participant")) +
    facet_wrap(~Gender, ncol=2, scales="free_y") +
    theme_minimal() +
    theme(panel.grid.major.y = element_blank(),
          panel.border = element_blank(),
          axis.line.x = element_blank(),
          axis.text.y = element_blank()) +
    labs(title = paste0(target, " by Participant"), x="Difference (Photograph - AI-Generated)", y="Participants")

  p1 / p2 + plot_layout(heights = c(2, 1))
}

# remove other 
arousal_desc <- df |> 
  filter(Gender != "Other") |> 
  plot_descriptive("Arousal")

arousal_desc
```

### Whole Sample

This model examines the effect of Gender and condition on Arousal, accounting for random variability due to participants and items (i.e., random effects).

<!-- The intercept is Male and photograph.  -->
Women rated 'photographs' significantly lower in arousal than men.
Men rated 'photographs' significantly higher in arousal than 'AI-generated' images.


The analysis also examined the average marginal effect of the variable "Condition" (comparing AI-Generated to Photograph) separately for males and females. For males, the arousal is on average significantly lower (althoug only slighly) for AI-Generated images compared to Photograph images. For females, the arousal is on average slightly lower for AI-Generated images compared to Photograph images; however, this effect is not significant.


```{r}

m_arousal <- glmmTMB::glmmTMB(Arousal ~ Gender/ Condition + 
                                (1| Participant) + (1|Stimulus), family=glmmTMB::ordbeta(),
                              data=df, control = glmmTMB::glmmTMBControl(parallel = 8))

results_table(m_arousal)

marginaleffects::avg_slopes(m_arousal, variables="Condition", by="Gender") 
#   results_table()

```

### Moderators

This model explores whether various factors such as **attitudes towards AI, knowledge about AI, frequency of porn consumption, and sexual activity** moderate the relationship between gender, image relevance (specifically AI-generated versus photographs), and arousal ratings.

The analysis revealed a significant interaction effect only for **positive attitudes towards AI** among females. Specifically, females with higher positive attitudes towards AI rated AI-generated images as more arousing, relative to when they viewed photographs 

No other moderators showed statistically significant effects on arousal across the interactions of gender, condition (Ai-generated vs Photograph), and the respective moderators.

We also examined whether **feedback** moderates the relationship between gender and condition on arousal. Findings suggest that feedback moderates this relationship only for men. Specifically, males who reported finding AI-generated images as less and more arousing had lower and higher, respectively, arousal ratings for those images.

<!-- All significant findings for feedback  -->

<!-- 1.For Males, giving feedback indicating that AI-generated images were less attractive, influenced arousal ratings for images labeled as AI-generated. Specifically, males who reported finding AI-generated images as less arousing had lower arousal ratings for those images. 


<!-- 2. For Males, giving feedback indicating that AI-generated images were more attractive significantly influenced arousal ratings for images labeled as AI-generated. Specifically, males who reported finding AI-generated images more attractive had higher arousal ratings for these images.  -->


<!-- Note: The feedback that the difference between the conditions was subtle only had one value - i.e., False.  The feedback that some AI images were arousing and that no AI images were arousing also only had one value - i.e., False -->


```{r}
test_moderator <- function(df, outcome="Arousal", moderator="BAIT_Visual") {
  f <- paste0(outcome, " ~ Gender / (Condition * ", moderator, ") + (Condition | Participant) + (1|Stimulus)")
  r <- glmmTMB::glmmTMB(as.formula(f),
                      data = df,
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8)) |>
    parameters::parameters() |> 
    as.data.frame() |> 
    select(-df_error, -Effects, -Group, -Component, -SE)
  r$Moderator <- moderator
  r$Outcome <- outcome
  insight::format_table(r[c(7, 8), ])
}


moderator_results <- data.frame()
for(m in c("BAIT_Visual", "BAIT_Text", "BAIT_ExpertAI", "BAIT_Positive", "BAIT_Negative", "PornFrequency", "SexualActivity")) {
  moderator_results <- rbind(moderator_results,
                             test_moderator(df, "Arousal", m))
}

display(moderator_results)
```


```{r}
feedback_results <- data.frame()
for(m in c("Feedback_NoFacesAttractive", "Feedback_SomeFacesAttractive", "Feedback_AIMoreAttractive", "Feedback_AILessAttractive", "Feedback_DiffObvious", "Feedback_DiffNone" ,
           "Feedback_LabelsIncorrect", "Feedback_LabelsReversed", "Feedback_AllReal", "Feedback_AllFake", "AllRealConfidence", "AllFakeConfidence" ,  "Enjoyment",
           
           ## New feedback
           "Feedback_AIMoreArousing", "Feedback_AILessArousing"
           
           )){ 
  feedback_results <- rbind(feedback_results,
                            test_moderator(df, "Arousal", m))
}
display(feedback_results)
```

### Believed

<!-- To DO -->

```{r}
  m <- glmmTMB::glmmTMB(Arousal ~ Gender / Condition + (1|Participant) + (1|Stimulus),
                        data=filter(df, ConditionBelief == "True"), 
                        family=glmmTMB::ordbeta(),
                        control = glmmTMB::glmmTMBControl(parallel = 8))
  
  results_table(m)
```

```{r}

 moderator_believed <- data.frame()
  for(m in c("BAIT_Visual", "BAIT_Text", "BAIT_ExpertAI",
             "BAIT_Positive", "BAIT_Negative",
             "PornFrequency", "SexualActivity", 
             "Feedback_CouldDiscriminate", "Feedback_CouldNotDiscriminate",
             "Feedback_AIMoreArousing", "Feedback_AILessArousing", 
             "Feedback_AIMoreAttractive", "Feedback_AILessAttractive",
             "Feedback_LabelsIncorrect", "Feedback_LabelsReversed")) {
    moderator_believed <- rbind(moderator_believed,
                               test_moderator(filter(df, ConditionBelief == "True"), "Arousal", m))
  }
  
  display(filter(moderator_believed, p < .1))

```

## Enticement 

Enticment ratings differ by whether the images were preceeded by 'photograph' or by 'ai-generated'.


```{r}
#| fig-height: 12
#| fig-width: 7

enticement_desc <- plot_descriptive(df, "Enticing")
enticement_desc
```


### Whole Sample

This model examines how Gender and Condition influence enticement ratings, treating participant and items as random effects.

<!-- Key Findings: -->

There was a significant interaction between gender and image condition, whereby men were less enticed by AI-generated images, whereas women showed no significant difference in enticement based on image condition. Across both conditions, women rated the images as less enticing overall than men.

We also analyzed the average marginal effect of the variable “Condition” (comparing AI-Generated to Photograph) separately for males and females.

For males, enticement ratings are significantly lower on average for AI-Generated images compared to Photograph images. For females, enticement ratings are slightly lower on average for AI-Generated images compared to Photograph images, although this difference is not statistically significant.

**Note**. 'Other' was removed due to the very small percentage of individuals identifying as such. 

```{r}
m_enticement <- glmmTMB::glmmTMB(Enticing ~ Gender / Condition + 
                                   (1 | Participant) + (1|Stimulus),
                      data=df, family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

results_table(m_enticement)

marginaleffects::avg_slopes(m_enticement, variables="Condition", by="Gender", re.form=NA)
```

### Moderators

We examined whether **attitudes towards AI, porn frequency, and sexual activity** moderated the relationship between the predictors (sex, relevance, condition) and enticement ratings. 

Looking at **feedback as a moderator**, the results showed that enticement ratings for images labeled AI-generated were moderated by the feedback reporting attitudes towards AI, but this was only significant for women. Specifically, women who reported that having more positive and negative attitudes towards AI, rated these images higher, and lower, in enticement compared to images labeled as photographs.

```{r}
for(m in c("BAIT_Visual", "BAIT_Text", "BAIT_ExpertAI",
           "BAIT_Positive", "BAIT_Negative",
           "PornFrequency", "SexualActivity")) {
  moderator_results <- rbind(moderator_results,
                             test_moderator(df, "Enticing", m))
}

display(filter(moderator_results, Outcome == "Enticing"))
```


```{r}
for(m in c("Feedback_CouldDiscriminate", "Feedback_CouldNotDiscriminate",
           "Feedback_AIMoreArousing", "Feedback_AILessArousing",
           "Feedback_AIMoreAttractive", "Feedback_LessArousing",
           "Feedback_LabelsIncorrect", "Feedback_LabelsReversed")) {
  feedback_results <- rbind(feedback_results,
                            test_moderator(df, "Enticing", m))
}
display(filter(feedback_results, Outcome == "Enticing"))
```


```{r}
m <- glmmTMB::glmmTMB(Enticing ~ Gender / (Condition * SexualActivity) + (Condition | Participant) + (1|Stimulus),
                      data=filter(df, ConditionBelief == "True"), 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

results_table(m)

sex_act_plot<- estimate_relation(m, length=20) |> 
  ggplot(aes(x=SexualActivity_num, y=Predicted)) +
  geom_ribbon(aes(ymin=CI_low, ymax=CI_high, fill=Condition), alpha=0.2) +
  geom_line(aes(color=Condition)) +
  facet_grid(~Sex)

sex_act_plot
```
