---
title: "Stimuli Selection"
format:
  html:
    embed-resources: true
editor_options: 
  chunk_output_type: console
---

```{r}
#| include: false
#| code-fold: true

library(tidyverse)
library(easystats)
library(ggrepel)


napsero <- readxl::read_excel("norms_napsero.XLSX", sheet = "Ratings") |>
  full_join(readxl::read_excel("norms_napsero.XLSX", sheet = "Image parameters"), by = join_by("ID", "Category")) |>
  select(-contains("_SD")) |>
  rename(Orientation = `V/H`,
         Hetero_Men_Valence = val_M_HeM,
         Hetero_Women_Valence = val_M_HeF,
         Homo_Men_Valence = val_M_HoM,
         Homo_Women_Valence = val_M_HoF,
         Hetero_Men_Arousal = aro_M_HeM,
         Hetero_Women_Arousal = aro_M_HeF,
         Homo_Men_Arousal = aro_M_HoM,
         Homo_Women_Arousal = aro_M_HoF) |>
  mutate(across(c("Luminance", "Contrast", "JPEG_size80", "LABL", "LABA", "LABB", "Entropy"), as.numeric),
         Description = NA)
```


## Selection

### Select based on norms
```{r}
men <- napsero |>
  filter(Category %in% c("Female", "Opposite-sex Couple")) |>
  group_by(Category) |>
  slice_max(Hetero_Men_Arousal, n=25, with_ties = FALSE) |>
  pull(ID)

homo_men <- napsero |>
  filter(Category %in% c("Male", "Male Couple")) |>
  group_by(Category) |>
  slice_max(Homo_Men_Arousal, n=25, with_ties = FALSE) |>
  pull(ID) 

women <- napsero |>
  filter(Category %in% c("Male", "Opposite-sex Couple")) |> 
  group_by(Category) |> 
  slice_max(Hetero_Women_Arousal, n=25, with_ties = FALSE) |>
  pull(ID) 

homo_women <- napsero |>
  filter(Category %in% c("Female", "Female Couple")) |>
  group_by(Category) |>
  slice_max(Homo_Women_Arousal, n=25, with_ties = FALSE) |>
  pull(ID) 


selected_erotic <- c(men, women, homo_men,homo_women)

cat(
  paste0("N (men) = ", length(men), "\nN (homo_men) = ", length(homo_men),  "\nN (women) = ", length(women), "\nN (homo_women) = ", length(homo_women))
)
```

### Visualization

```{r}
#| fig.width: 10
#| fig.height: 8
#| dpi: 300
#| message: false

dat <- napsero |>
  select(ID, Category, ends_with("_Arousal"), ends_with("_Valence")) |> 
  pivot_longer(cols = c("Hetero_Men_Valence", "Hetero_Men_Arousal", "Hetero_Women_Valence", "Hetero_Women_Arousal", "Homo_Men_Valence", "Homo_Men_Arousal", "Homo_Women_Valence", "Homo_Women_Arousal")) |>
  separate(name, into=c("Participant1", "Participant2", "Variable")) |>
  mutate("Target" = paste0(Participant1, "_", Participant2)) |> 
  select(-Participant1, -Participant2) |> 
  pivot_wider(names_from=Variable, values_from=value) |> 
  mutate(Selected = case_when(
    Target == "Hetero_Men" & ID %in% men ~ TRUE,
    Target == "Homo_Men" & ID %in% homo_men ~ TRUE,
    Target == "Hetero_Women" & ID %in% women ~ TRUE,
    Target == "Homo_Women" & ID %in% homo_women ~ TRUE,
    .default = FALSE
  ))



dat |> 
  ggplot(aes(x = Valence, y = Arousal)) +
  geom_point(data=filter(dat, Selected==FALSE),
             aes(shape = Selected, color = Category), size = 4, alpha = 0.3) +
  geom_point(data=filter(dat, Selected==TRUE),
             aes(shape = Selected, color = Category), size = 4, alpha = 0.8) +
  facet_wrap(~Target) +
  ggside::geom_ysidedensity(data=filter(dat, Selected==TRUE), 
                            aes(color = Category),
                            key_glyph = draw_key_blank, alpha = 0.0) +
  ggside::geom_xsidedensity(data=filter(dat, Selected==TRUE), 
                            aes(color = Category), 
                            key_glyph = draw_key_blank, alpha = 0.0)  +
  scale_shape_manual(values = c("TRUE" = 20, "FALSE" = 4)) +
  scale_color_manual(values = c(
    "Opposite-sex Couple" = "#673AB7", "Male Couple" = "#3F51B5", "Female Couple" = "#9C27B0",
    "Female" = "#E91E63", "Male" = "#2196F3", "Non-erotic"="grey")) +
  guides(shape = guide_legend(override.aes = list(color = "white"))) +
  theme_abyss() +
  theme(ggside.panel.grid.major = element_blank(), 
        ggside.axis.text = element_blank(),
        ggside.axis.line = element_blank())
```


## Final Selection

- ID: picture category and number
- V/H: vertical / horizontal
- Av/Ap: avoidance - approach dimension
- M: mean
- SD: standard deviation
- JPEG_size80: index of overall complexity
- LABL: luminance in CIE L*a*b color space
- LABA: the amount of red color CIE L*a*b color space
- LABB: the amount of the green color CIE L*a*b color space
- Entropy: the amount of complexity in gray scale. Images with high entropy are images that are more "noisy" and have a high degree of contrast.

```{r}
#| code-fold: true

selection <- napsero |> 
  filter(ID %in% selected_erotic)

write.csv(selection, "stimuli_data.csv", row.names=FALSE)
knitr::kable(selection)
```


```{r}
#| code-fold: true
json <- selection |> 
  select(stimulus=ID, Category, Orientation) |> 
  jsonlite::toJSON()
  
write(paste("var stimuli_list = ", json), "stimuli_list.js")
```


```{r}
#| code-fold: true
path_ero <- "C:/Dropbox/RECHERCHE/docs/Stimuli/NAPS/NAPS_ERO/"
path_naps <- "C:/Dropbox/RECHERCHE/docs/Stimuli/NAPS/NAPS/"

# Remove all current files
unlink("../stimuli/*")

# Copy each file
for(file in selected) {
  if(str_detect(file, "Male|Female")) {
    file.copy(paste0(path_ero, file), "../stimuli/")
  } else {
    file.copy(paste0(path_naps, file), "../stimuli/")
  }
}
```
