---
title: "FictionEro- Study 2"
editor: source
editor_options: 
  chunk_output_type: console
format:
  html:
    toc: true
    code-fold: true
    self-contained: false
execute: 
  cache: false
  cache-lazy: false
---

# Data Preparation

```{r libraries}
#| message: false
#| warning: false

library(dplyr)
library(tidyverse)
library(easystats)
library(patchwork)
library(ggside)
library(gt)
library(ggdist)
library(posterior)
library(forcats)

options(mc.cores = parallel::detectCores(),
        brms.backend = "cmdstanr",
        width = 300)
```

```{r functions}

results_table <- function(model, effects="fixed", filter=NULL) {
  if("marginaleffects" %in% class(model)) {
    model |> 
      parameters::parameters() |> 
      as.data.frame() |> 
      select(-Parameter, -SE, -S, z=Statistic) |> 
      insight::format_table() |> 
      parameters::display()
  } else {
    display(parameters::parameters(model, effects=effects, keep=filter))
  }
}

# Parameters tables for the models 
params_table <- function(m) {
  # d <- as.data.frame(m, variable = insight::find_parameters(m, effects = "fixed", flatten  = TRUE))
  t <- bayestestR::describe_posterior(m, effects = "fixed", component = "all", ci_method = "hdi", test = "p_direction")
  out <- insight::format_table(t)
  out |> 
    mutate(col = t$pd) |> 
    gt::gt() |> 
    gt::data_color(columns = "col", method = "numeric", target_columns = "pd", 
                   row = col > 0.95, palette = "yellow") |> 
    gt::data_color(columns = "col", method = "numeric", target_columns = "pd", 
                   row = col > 0.97, palette = "green") |> 
    gt::cols_hide("col")
}

# Random effects table
table_dvour <- function(g) {
  performance::performance_dvour(g) |> 
    arrange(desc(D_vour)) |> 
    gt::gt() |> 
    gt::data_color("D_vour", palette = c("red","green"), domain = c(0, 1)) |> 
    gt::fmt_auto()
}

```

```{r data study2}
#| message: false
#| warning: false

dfsub2 <- read.csv("https://raw.githubusercontent.com/RealityBending/FictionEro/refs/heads/main/study2/data/data_participants.csv")
df2 <- read.csv("https://raw.githubusercontent.com/RealityBending/FictionEro/refs/heads/main/study2/data/data.csv") |> 
  right_join(
    select(dfsub2, Participant, Mobile, starts_with(c("Feedback_","BAIT")), COPS_Frequency, SexualActivity,- Feedback_Text),
    by = "Participant") |> 
  datawizard::rescale(select= c("Arousal", "Enticing", "Valence"), range=c(0, 6), to=c(0,1)) |>
  datawizard::rescale(select= c("Realness"), range=c(-3,3), to=c(0,1)) |>
  filter(SexualOrientation == "Heterosexual") |> # Keep only heterosexuals
  mutate(Gender =  fct_relevel(Gender, "Male", "Female"),
         Condition = case_when(
           Condition == "Fiction" ~ "AIGenerated",
           Condition == "Reality" ~ "Photograph"), 
         Condition = fct_relevel(Condition, "Photograph", "AIGenerated"),
         ConditionBelief = case_when(
               Condition == "Photograph" & Realness > 0.5 ~ "True", 
               Condition == "AIGenerated" & Realness < 0.5 ~ "True", 
               .default = "False"),
        Type = case_when(
           Category %in% c("Female", "Male") ~ "Single",
           .default = "Couple"),
         Type = as.factor(Type),
        Type = fct_relevel(Type, "Single", "Couple"),
         PornFrequency = as.numeric(as.factor(COPS_Frequency)),
         SexualActivity_num = as.numeric(as.factor(SexualActivity)),
         across(starts_with("Feedback_"), as.factor),
         across(starts_with("Feedback_"), function(x) {fct_relevel(x, "False", "True")})) |>
    rename(Item = Stimulus,
           Enticement = Enticing,
           AllRealConfidence = "Feedback_AllRealConfidence",
           AllFakeConfidence = "Feedback_AllFakeConfidence",
           Enjoyment = "Feedback_Enjoyment") 



## compute based on higher dimensions

 
 df2$BAIT_VideosIssues <- 6 - df2$BAIT_VideosIssues
df2$BAIT_TextIssues <- 6 - df2$BAIT_TextIssues

df2$BAIT_Dangerous <- 6 - df2$BAIT_Dangerous
df2$BAIT_Worry <- 6 - df2$BAIT_Worry

df2$BAIT_ImageDistinctionBad <- 6 - df2$BAIT_ImageDistinctionBad
df2$BAIT_TextDifferentiation <- 6 - df2$BAIT_TextDifferentiation

df2$BAIT_UniqueHuman <- 6 - df2$BAIT_UniqueHuman
df2$BAIT_ImpersonalAI <- 6 - df2$BAIT_ImpersonalAI
df2$BAIT_EmotionalHuman <- 6 - df2$BAIT_EmotionalHuman
df2$BAIT_PreferenceHuman <- 6 - df2$BAIT_PreferenceHuman
df2$BAIT_TrustHuman <- 6 - df2$BAIT_TrustHuman


df2$BAIT_Expectations <- rowMeans(select(df2, BAIT_ImagesRealistic, BAIT_ImagesIssues,  BAIT_VideosIssues, BAIT_TextIssues, BAIT_VideosRealistic, BAIT_TextRealistic, BAIT_EnvironmentReal, BAIT_ImitatingReality), na.rm=TRUE)

df2$BAIT_Attitudes <- rowMeans(select(df2,BAIT_Worry, BAIT_Exciting, BAIT_Dangerous, BAIT_Benefit), na.rm=TRUE)

df2$BAIT_Expertise <- rowMeans(select(df2, BAIT_UserAI, BAIT_UnderstandingAI, BAIT_ExpertAI), na.rm=TRUE)

df2$BAIT_Discrimination <- rowMeans(select(df2,BAIT_ImageDistinctionEasy, BAIT_ImageDistinctionBad, BAIT_TextDifferentiation, BAIT_ContentDetection), na.rm=TRUE)

df2$BAIT_Bias <- rowMeans(select(df2,BAIT_InnovativeAI, BAIT_UniqueHuman, BAIT_EmotionalHuman, BAIT_InterestingAI, BAIT_TrustHuman, BAIT_ImpersonalAI, BAIT_PreferenceHuman), na.rm=TRUE)


df2$BAIT_Total <- rowMeans(select(df2, BAIT_Expectations, BAIT_Attitudes, BAIT_Expertise, BAIT_Discrimination, BAIT_Bias), na.rm=TRUE)
```

# Questionnaires

::: panel-tabset
## BAIT

```{r}
#| message: false
#| warning: false
#| output: false

## compute based on higher dimensions
dfsub2$BAIT_ImagesIssues <- 6 - dfsub2$BAIT_ImagesIssues
dfsub2$BAIT_VideosIssues <- 6 - dfsub2$BAIT_VideosIssues
dfsub2$BAIT_TextIssues <- 6 - dfsub2$BAIT_TextIssues

dfsub2$BAIT_Dangerous <- 6 - dfsub2$BAIT_Dangerous
dfsub2$BAIT_Worry <- 6 - dfsub2$BAIT_Worry

dfsub2$BAIT_ImageDistinctionBad <- 6 - dfsub2$BAIT_ImageDistinctionBad
dfsub2$BAIT_TextDifferentiation <- 6 - dfsub2$BAIT_TextDifferentiation

dfsub2$BAIT_UniqueHuman <- 6 - dfsub2$BAIT_UniqueHuman
dfsub2$BAIT_ImpersonalAI <- 6 - dfsub2$BAIT_ImpersonalAI
dfsub2$BAIT_EmotionalHuman <- 6 - dfsub2$BAIT_EmotionalHuman
dfsub2$BAIT_PreferenceHuman <- 6 - dfsub2$BAIT_PreferenceHuman
dfsub2$BAIT_TrustHuman <- 6 - dfsub2$BAIT_TrustHuman


BAIT_Expectations <- select(dfsub2, c("BAIT_ImagesRealistic", "BAIT_ImagesIssues",  "BAIT_VideosIssues", "BAIT_TextIssues", "BAIT_VideosRealistic", "BAIT_TextRealistic", "BAIT_EnvironmentReal", "BAIT_ImitatingReality"))

BAIT_Attitudes <- select(df2, c("BAIT_Worry", "BAIT_Exciting", "BAIT_Dangerous", "BAIT_Benefit"))

BAIT_Expertise <- select(df2, c("BAIT_UserAI", "BAIT_UnderstandingAI", "BAIT_ExpertAI"))

BAIT_Discrimination <- select(df2,c("BAIT_ImageDistinctionEasy", "BAIT_ImageDistinctionBad", "BAIT_TextDifferentiation", "BAIT_ContentDetection"))

BAIT_Bias <- select(df2,c("BAIT_InnovativeAI", "BAIT_UniqueHuman", "BAIT_EmotionalHuman", "BAIT_InterestingAI", "BAIT_TrustHuman", "BAIT_ImpersonalAI", "BAIT_PreferenceHuman"))

BAIT_Expectations_o <- psych::omega(BAIT_Expectations, nfactors = 1)
BAIT_Attitudes_o <-psych::omega(BAIT_Attitudes, nfactors = 1)
BAIT_Expertise_o <- psych::omega(BAIT_Expertise, nfactors = 1)
BAIT_Discrimination_o <- psych::omega(BAIT_Discrimination, nfactors = 1)
BAIT_Bias_o <- psych::omega(BAIT_Bias, nfactors = 1)
```

McDonald's Omega (⍵) total was acceptable for all the BAIT dimensions (Expectations about AI ⍵ = `r round(BAIT_Expectations_o$omega.tot,2)`, Attitudes towards AI ⍵ = `r round(BAIT_Attitudes_o$omega.tot, 2)`, Expertise about AI ⍵ = `r round(BAIT_Expertise_o$omega.tot, 2)`, Bias against AI ⍵ = `r round( BAIT_Bias_o$omega.tot, 2)`), except the Discrimination ability of AI output which showed good internal consistency (⍵ =`r round( BAIT_Discrimination_o$omega.tot, 2)`).

## COPS

```{r}
#| message: false
#| warning: false
#| output: false

dfsub2 <- dfsub2 |>
  mutate(COPS_Frequency = case_when(
    COPS_Frequency == "0. I haven't viewed pornography in the past 30 days" ~ 0,
    COPS_Frequency =="1. I viewed pornography once in the past 30 days" ~ 1,
    COPS_Frequency == "2. I viewed pornography twice in the past 30 days" ~2,
    COPS_Frequency =="3. I viewed pornography weekly" ~3,
    COPS_Frequency == "4. I viewed pornography multiple times a week " ~ 4,
    COPS_Frequency == " 5. I viewed pornography daily" ~5,
    COPS_Frequency == "6. I viewed pornography multiple times a day" ~ 6),
    SexualActivity = case_when(
      SexualActivity == "1. Less than 24h ago" ~ 1 ,
      SexualActivity == "2. Within the last 3 days" ~ 2,
      SexualActivity == "3. Within the last week" ~ 3,
      SexualActivity == "4. Within the last month" ~ 4,
      SexualActivity == "5. Within the last year" ~ 5,
      SexualActivity == "6. More than a year ago" ~ 5,
      .default = NA)
    )


COPS <- select(dfsub2, "COPS_Frequency", "SexualActivity")

Cops_o <- psych::omega(COPS, nfactors = 1)
```

McDonald's Omega (⍵) total was also poor for the COPS (⍵ =`r round(Cops_o$omega.tot,2)`) in study 2.
:::

# Manipulation Checks

```{r ratebelief 2}

rate2 <- table(df2$Feedback_AllReal)["True"] / sum(table(df2$Feedback_AllReal))
```

In study 2 (i.e., gave feedback that all images were real images) was `r round(mean(rate2) * 100, 1)`%.

```{r}
df2_log <- df2 |>
  mutate(ConditionBelief = case_when(
               Condition == "Photograph" & Realness > 0.5 ~ 0, 
               Condition == "AIGenerated" & Realness < 0.5 ~ 0, 
               .default = 1))
               
               
m_log <- glmmTMB::glmmTMB(ConditionBelief ~ Gender * Type + (1 | Participant), data = df2_log, family = binomial)

results_table(m_log)
```

There is no clear evidence that Gender, Type, or their interaction predicts ConditionBelief.

::: panel-tabset
## Arousal

```{r dist arousal 2}
#| fig-width: 12
arousal_dist2 <- df2 |>
  ggplot(aes(x=Arousal, fill = Condition)) +
  geom_bar(position = "identity", alpha = 0.5, colour = "black") +
  scale_y_sqrt(expand = c(0, 0)) +
  scale_x_continuous(breaks = c(0, 1)) +
  labs(title = "Arousal Study 2", ) +
  facet_wrap(~Gender) +
  scale_fill_manual(values=c("AIGenerated"="#2196F3", "Photograph"="#F44336")) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5, face="bold"))

arousal_dist2
```

```{r arousal 2 t_test}
#| message: false

dfsub2_arousal <- dfsub2 |>
  right_join(
    df2|>
      group_by(Participant, Condition)|>
      summarise(mean_arousal = mean(Arousal, na.rm = TRUE), .groups = "drop") |>
      pivot_wider(names_from = Condition, 
                  names_prefix = "mean_Arousal_", 
                  values_from = mean_arousal) |>
      mutate(diff_arousal = `mean_Arousal_AIGenerated` - mean_Arousal_Photograph)) |>
   mutate(Feedback_AILessArousing = as.factor(Feedback_AILessArousing)) |>
    as.data.frame()

df2 |>
  group_by(Feedback_AILessArousing, Condition ) |>
  summarise(mean_Arousal = mean(Arousal, na.rm = TRUE), 
            sd_Arousal = sd(Arousal, na.rm = TRUE),.groups = "drop") |>
  gt() |>
  fmt_number(decimals = 3, use_seps = FALSE)


ttest2 <- BayesFactor::ttestBF(dfsub2_arousal$diff_arousal, dfsub2_arousal$Feedback_AILessArousing)
model_parameters(ttest2)

```

```{r arousal 2 diff plot}
diff_plot2 <- dfsub2_arousal |> 
  ggplot(aes(x = Feedback_AILessArousing, y = diff_arousal, fill = Feedback_AILessArousing)) +
  geom_boxplot(width = 0.4, alpha = 0.7) +
  geom_jitter(width = 0.2, alpha = 0.1, size = 1) +
  stat_summary(fun = mean, geom = "point", shape = 23, size = 2, fill = "black") +
  labs(
    title = "Study 2",
    x = "Participant said AI is less arousing",
    y = "Arousal Difference (AI - Photo)"
  ) +
  scale_fill_manual(values = c("True" = "#E66100", "False" = "#5D3A9B")) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    legend.position = "none"
  )

diff_plot2
```

## Enticement

```{r dist enticement 2}
#| fig-width: 12
enticement_dist2 <- df2 |>
  ggplot(aes(x=Enticement, fill = Condition)) +
  geom_bar(position = "identity", alpha = 0.5, colour = "black") +
  scale_y_sqrt(expand = c(0, 0)) +
  scale_x_continuous(breaks = c(0, 1)) +
  labs(title = "Enticement Study 2", ) +
  facet_wrap(~Gender) +
  scale_fill_manual(values=c("Photograph"="#F44336", "AIGenerated"="#2196F3")) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5, face="bold"))

enticement_dist2
```

```{r enticement 2 t_test}
#| message: false

dfsub2_enticement <- dfsub2 |>
  right_join(
    df2|>
      group_by(Participant, Condition)|>
      summarise(mean_Enticement = mean(Enticement, na.rm = TRUE), .groups = "drop") |>
      pivot_wider(names_from = Condition, 
                  names_prefix = "mean_Enticement_", 
                  values_from = mean_Enticement) |>
      mutate(diff_enticement = `mean_Enticement_AIGenerated` - mean_Enticement_Photograph)) |>
   mutate(Feedback_AILessArousing = as.factor(Feedback_AILessArousing)) |>
    as.data.frame()

df2 |>
  group_by(Feedback_AILessArousing, Condition ) |>
  summarise(mean_Enticement = mean(Enticement, na.rm = TRUE), 
            sd_Enticement = sd(Enticement, na.rm = TRUE),.groups = "drop") |>
  gt() |>
  fmt_number(decimals = 3,
    use_seps = FALSE)


ttest2 <- BayesFactor::ttestBF(dfsub2_enticement$diff_enticement, dfsub2_enticement$Feedback_AILessArousing)
model_parameters(ttest2)
```

```{r enticement 2 diff plot}
diff_plot2 <- dfsub2_enticement |> 
  ggplot(aes(x = Feedback_AILessArousing, y = diff_enticement, fill = Feedback_AILessArousing)) +
  geom_boxplot(width = 0.4, alpha = 0.7) +
  geom_jitter(width = 0.2, alpha = 0.1, size = 1) +
  stat_summary(fun = mean, geom = "point", shape = 23, size = 2, fill = "black") +
  labs(
    title = "Study 2",
    x = "Participant said AI is less arousing",
    y = "Enticement Difference (AI - Photo)"
  ) +
  scale_fill_manual(values = c("True" = "#E66100", "False" = "#5D3A9B")) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    legend.position = "none"
  )

diff_plot2
```

## Valence

```{r dist valence 2}
#| fig-width: 12
valence_dist2 <- df2 |>
  ggplot(aes(x=Valence, fill = Condition)) +
  geom_bar(position = "identity", alpha = 0.5, colour = "black") +
  scale_y_sqrt(expand = c(0, 0)) +
  scale_x_continuous(breaks = c(0, 1)) +
  labs(title = "Valence Study 2", ) +
  facet_wrap(~Gender) +
  scale_fill_manual(values=c("Photograph"="#F44336", "AIGenerated"="#2196F3")) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5, face="bold"))

valence_dist2
```

```{r valence 2 t_test}
#| message: false

dfsub2_valence <- dfsub2 |>
  right_join(
    df2|>
      group_by(Participant, Condition)|>
      summarise(mean_Valence = mean(Valence, na.rm = TRUE), .groups = "drop") |>
      pivot_wider(names_from = Condition, 
                  names_prefix = "mean_Valence_", 
                  values_from = mean_Valence) |>
      mutate(diff_valence = `mean_Valence_AIGenerated` - mean_Valence_Photograph))  |>
   mutate(Feedback_AILessArousing = as.factor(Feedback_AILessArousing)) |>
    as.data.frame()

df2 |>
  group_by(Feedback_AILessArousing, Condition ) |>
  summarise(mean_Valence = mean(Valence, na.rm = TRUE), 
            sd_valence = sd(Valence, na.rm = TRUE),.groups = "drop") |>
  gt() |>
  fmt_number(decimals = 3, use_seps = FALSE)

ttest2 <- BayesFactor::ttestBF(dfsub2_valence$diff_valence, dfsub2_valence$Feedback_AILessArousing)
model_parameters(ttest2)
```

```{r valence 2 diff plot}
diff_plot2 <- dfsub2_valence |> 
  ggplot(aes(x = Feedback_AILessArousing, y = diff_valence, fill = Feedback_AILessArousing)) +
  geom_boxplot(width = 0.4, alpha = 0.7) +
  geom_jitter(width = 0.2, alpha = 0.1, size = 1) +
  stat_summary(fun = mean, geom = "point", shape = 23, size = 2, fill = "black") +
  labs(
    title = "Study 2",
    x = "Participant said AI is less arousing",
    y = "Valence Difference (AI - Photo)"
  ) +
  scale_fill_manual(values = c("True" = "#E66100", "False" = "#5D3A9B")) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    legend.position = "none"
  )

diff_plot2
```
:::

# Models
::: panel-tabset
## Arousal

```{r arousal 2 by condition belief plot }
df2 |> 
  ggplot(aes(x = Gender, y = Arousal, fill = ConditionBelief)) +
  geom_violin(position = position_dodge(width = 1), alpha = 0.7, trim = FALSE) +
  stat_pointinterval(position = position_dodge(width = 1),point_size = 1.5) +
  facet_grid( ~ Condition) +
  scale_fill_manual(values = c("True" = "#E66100", "False" = "#5D3A9B")) +
  theme_minimal(base_size = 14) +
  labs(title = "Arousal by Gender × Belief × Condition", subtitle ="Study 2", x = "Gender", y = "Arousal",fill = "Condition Belief")

```

```{r arousal 2 model load}
#| cache: false
 
m <- readRDS("models/ZOIB/ModelArousal_2_ZOIB.rds")
```

```{r arousal 2 model analysis}
params_table(m)
summary(m, robust = TRUE)
```

### Marginal contrasts

::: panel-tabset
#### Effect of Relevance

```{r arousal 1 est cont relevance}
#| message: false
#| warning: false

estimate_contrasts(m, contrast = "Relevance", by="Gender", backend = "emmeans") 
```

#### Effect of Condition

```{r arousal 1 est cont condition }
#| message: false
#| warning: false

estimate_contrasts(m, contrast = "Condition", by="Gender", backend = "emmeans") 
```

#### Effect of Condition depending on congruency

```{r arousal 2 est cont}
estimate_contrasts(m, contrast = "Condition", by=c("Gender", "ConditionBelief"), backend = "emmeans")
```

```{r arousal 2 model plot}
#| message: false
#| warning: false

pred_a2 <- modelbased::estimate_means(m, by=c("Gender", "Condition", "ConditionBelief"), backend = "emmeans") |>
  as.data.frame()


pd <- data.frame(label=c("pd = 100%", "pd = 99.71%"),
                 Gender = c("Male", "Male"),
                 ConditionBelief = c("Congruent", "Incongruent"),
                 y =c(0.60, 0.55))


pred_a2 |>
  mutate(Gender = fct_relevel(Gender, "Male", "Female"),
         ConditionBelief = fct_recode(ConditionBelief, "Congruent" = "True", "Incongruent" = "False"),
         ConditionBelief = fct_relevel(ConditionBelief, "Congruent", "Incongruent")) |> 
  ggplot(aes(x=ConditionBelief, y=Probability)) +
    geom_hline(yintercept=0, color="darkgrey") +
  geom_line(aes(group=Condition, color=Condition), position = position_dodge(width=0.2), alpha=0.8, linewidth=0.2) +
  geom_pointrange(aes(ymin = CI_low, ymax=CI_high, color=Condition), position = position_dodge(width=0.2), size=0.6)+
  geom_rect(data=data.frame(Probability=0.1, Gender=as.factor("Male"), ConditionBelief="Congruent"),
            aes(xmin = 0.8, xmax = 1.2,ymin=0.35, ymax=0.55), color="#8BC34A", alpha=0, linewidth = 1.2) +
  geom_rect(data=data.frame(Probability=0.1, Gender=as.factor("Male"), ConditionBelief="Congruent"),
            aes(xmin = 1.8, xmax = 2.2,ymin=0.32, ymax=0.52), color="#8BC34A", alpha=0, linewidth = 1.2) +
   geom_text(data=pd, aes(label = label, y=y), hjust=0.5, size = 3.5) +
  
  facet_grid(~Gender, switch = "y") +
  scale_y_continuous(limits=c(0, 1)) +
  scale_color_manual(values=c("AIGenerated"="#2196F3", "Photograph"="#F44336")) +
  theme_minimal() +
    theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        axis.text.y = element_text(size = 10, face = "bold"),
        strip.placement = "outside",
        strip.background.x = element_rect(fill=c("lightgrey"), color=NA),
        strip.text.x = element_text(size = 12, face = "bold"),
        strip.text.y = element_text(size = 10, face = "bold"),
        axis.text.x = element_text(hjust=1,face = "bold", vjust=1.1, size=10, color="black"),
        legend.text = element_text(size = 10),
        legend.position = "bottom") +
  labs(color="Images presented as:")


```
:::

### Inter-individual Variability

::: panel-tabset
#### Random effects

```{r arousal 2 d_vour}
m <- modelbased::estimate_grouplevel(m)
table_dvour(m)
```

#### Participant effects

```{r arousal 2 ppt effects}
colors2 <- c("Intercept" = "#9C27B0", "AI-Generated" = "#FF9800")


## plot for participant effects
p_dvour <- function(m, colors){
  m |>
    mutate(
      Group = fct_relevel(Group, "Participant", "Item"),
      Parameter = fct_relevel(Parameter, "Intercept", "ConditionAIGenerated"),
    Parameter = fct_recode(
      Parameter,
      `AI-Generated` = "ConditionAIGenerated"))|>
    ggplot(aes(x = Median , y = Level)) +
    geom_pointrange(
      aes(xmin = CI_low, xmax = CI_high, color = Parameter),
      linewidth = 0.3, size = 0.05
    ) +
    facet_grid(Group ~ Parameter, scales = "free", switch = "both") +
    ggside::ggside(scales = "free") +
    ggside::geom_xsidedensity(aes(fill = Parameter), color = NA) +
    # scale_x_continuous(limits = c(-2,2), breaks = seq(-2, 2, 1)) +
    scale_color_manual(values = colors) +
    scale_fill_manual(values = colors) +
    theme_minimal() +
    theme(
      axis.text.y = element_blank(),
      axis.ticks.y = element_blank(),
      strip.placement.x = "outside",
      strip.background = element_rect(fill = NA, color = NA),
      axis.title = element_blank(),
      panel.grid.minor = element_blank(),
      panel.grid.major.y = element_blank(),
      axis.text.x = element_text(hjust = 1, size =12 ),
      legend.position = "none")
}
```

```{r}
p_dvour(m, colors2)
```

:::

### Correlations (moderators)

```{r df 2 corr}
correlations2 <- df2 |>
  select(Participant, "BAIT_Attitudes", "BAIT_Expectations", "BAIT_Expertise", "BAIT_Discrimination", "BAIT_Bias", "BAIT_Total", "PornFrequency", "SexualActivity_num", "COPS_Frequency", "AllRealConfidence", "AllFakeConfidence", "Enjoyment", -"Bait_Duration") |>
  rename(SexualActivity = SexualActivity_num,
         SexualActivity_num)

corr_mod <- function(m, correlations){
  features1 <- reshape_grouplevel(m, indices = "Median", group = "Participant") |> 
  full_join(correlations, by = "Participant")  |>
  rename(`AI-Generated` = ConditionAIGenerated)
  

  cordata <- correlation::correlation(select(features1, -Participant), p_adjust = "none", redundant = TRUE) |> 
    correlation::cor_sort() |>
    correlation::cor_lower() |>
    as.data.frame() |>
      mutate(Parameter2 = fct_rev(Parameter2),
         Parameter1 = fct_relabel(Parameter1, \(x) gsub("_Intercept", "", x)),
         Parameter2 = fct_relabel(Parameter2, \(x) gsub("_Intercept", "", x)),
         Parameter1 = fct_relabel(Parameter1, \(x) gsub("_", " - ", x)),
         Parameter2 = fct_relabel(Parameter2, \(x) gsub("_", " - ", x)))
  
  p2_cor <- cordata |> 
    ggplot(aes(x=Parameter2, y = Parameter1)) +
    geom_tile(aes(fill = r)) +
    geom_text(aes(label = insight::format_value(r, 2, zap_small = TRUE, lead_zero = FALSE)), color = ifelse(cordata$p < 0.01, "black", "grey")) +
    scale_fill_gradient2(low = "blue", mid = "white", high = "red", midpoint = 0) +
    theme_minimal() +
    theme(
      axis.text.x = element_text(angle = 45, hjust = 1),
      axis.title.x = element_blank(),
      axis.title.y = element_blank(),
      legend.position = "none"
    )
  p2_cor
  
}

```

```{r arousal 2 corr}

corr_mod(m, correlations2)
```

### Marginal contrasts with Type

```{r arousal 2 model type load}
#| cache: false
 
m_type <- readRDS("models/ZOIB/ModelArousal_2_ZOIB_type.rds")

```

```{r arousal 2 type model analysis}
params_table(m_type)
summary(m_type, robust = TRUE)
# performance::performance(m)
```

::: panel-tabset
#### Effect of Relevance

```{r arousal 1 est cont relevance with type }
#| message: false
#| warning: false

estimate_contrasts(m_type, contrast = "Relevance", by=c("Gender", "Type"), backend = "emmeans") 
```

#### Effect of Condition

```{r arousal 1 est cont condition with Type }
#| message: false
#| warning: false

estimate_contrasts(m_type, contrast = "Condition", by=c("Gender", "Type"), backend = "emmeans") 
```

#### Effect of Condition depending on congruency

```{r arousal 2 type est cont}
estimate_contrasts(m_type, contrast = "Condition", by=c("Gender", "Type", "ConditionBelief"), backend = "emmeans")
```
:::

## Enticement

```{r enticement 2 by condition belief plot }
df2 |> 
  ggplot(aes(x = Gender, y = Enticement, fill = ConditionBelief)) +
  geom_violin(position = position_dodge(width = 1), alpha = 0.7, trim = FALSE) +
  stat_pointinterval(position = position_dodge(width = 1),point_size = 1.5) +
  facet_grid( ~ Condition) +
  scale_fill_manual(values = c("True" = "#E66100", "False" = "#5D3A9B")) +
  theme_minimal(base_size = 14) +
  labs(title = "Enticement by Gender × Belief × Condition", subtitle ="Study 2", x = "Gender", y = "Arousal",fill = "Condition Belief")

```


```{r enticement 2 model load}
#| cache: false
 
m <- readRDS("models/ZOIB/ModelEnticement_2_ZOIB.rds")
```

```{r enticement 2 model analysis}
params_table(m)
summary(m, robust = TRUE)
# performance::performance(m)
```

### Marginal Contrasts
::: panel-tabset

#### Effect of Relevance

```{r enticement 1 est cont relevance}
#| message: false
#| warning: false

estimate_contrasts(m, contrast = "Relevance", by="Gender", backend = "emmeans") 
```

#### Effect of Condition

```{r enticement 1 est cont condition }
#| message: false
#| warning: false

estimate_contrasts(m, contrast = "Condition", by="Gender", backend = "emmeans") 
```

#### Effect of Condition Depending on congruency

```{r enticement 2 est cont}
estimate_contrasts(m, contrast = "Condition", by=c("Gender", "ConditionBelief"), backend = "emmeans")
```

```{r enticement 2 model plot}
#| message: false
#| warning: false

pred_e2 <- modelbased::estimate_means(m, by=c("Gender", "Condition", "ConditionBelief"), backend = "emmeans") |>
  as.data.frame()

pd <- data.frame(label=c("pd = 100%", "pd = 99.2%", "pd = 99.8%"),
                 Gender = c("Male", "Female", "Male"),
                 ConditionBelief = c("Congruent", "Congruent", "Incongruent"),
                 y =c(0.65, 0.65, 0.6))


pred_e2 |>
  mutate(Gender = fct_relevel(Gender, "Male", "Female"),
         ConditionBelief = fct_recode(ConditionBelief, "Congruent" = "True", "Incongruent" = "False"),
         ConditionBelief = fct_relevel(ConditionBelief, "Congruent", "Incongruent")) |> 
  ggplot(aes(x=ConditionBelief, y=Probability)) +
    geom_hline(yintercept=0, color="darkgrey") +
  geom_line(aes(group=Condition, color=Condition), position = position_dodge(width=0.2), alpha=0.8, linewidth=0.2) +
  geom_pointrange(aes(ymin = CI_low, ymax=CI_high, color=Condition), position = position_dodge(width=0.2), size=0.2)+
  geom_text(data=pd, aes(y=y, label = label), hjust=0.5, size = 3.5) +
  geom_rect(data=data.frame(Probability=0.1, Gender=as.factor("Male"), ConditionBelief="Congruent"),
            aes(xmin = 0.8, xmax = 1.2,ymin=0.4, ymax=0.6), color="#8BC34A", alpha=0, linewidth = 1.2) +
  geom_rect(data=data.frame(Probability=0.1, Gender=as.factor("Female"), ConditionBelief="Congruent"),
            aes(xmin = 0.8, xmax = 1.2,ymin=0.4, ymax=0.6), color="#8BC34A", alpha=0, linewidth = 1.2) +
  facet_grid(~Gender, switch = "y") +
  scale_y_continuous(limits=c(0, 1), labels=scales::percent) +
  scale_color_manual(values=c("AIGenerated"="#2196F3", "Photograph"="#F44336")) +
  theme_minimal() +
    theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        axis.text.y = element_text(size = 8),
        strip.placement = "outside",
        strip.background.x = element_rect(fill=c("lightgrey"), color=NA),
        strip.text.x = element_text(size = 10, face= "bold"),
        strip.text.y = element_text(size = 10),
        axis.text.x = element_text(hjust=1, vjust=1.1, size=9, color="black", face = "bold"),
        legend.text = element_text(size = 10),
        legend.position = "bottom") +
  labs(color="Images presented as:")
```
:::

### Inter-individual Variability

::: panel-tabset
#### Random effects

```{r enticement 2  d_vour}
m <- modelbased::estimate_grouplevel(m)
table_dvour(m)
```

#### Participant effects

```{r enticement 2 ppt effects}
p_dvour(m, colors2)
```

:::

### Correlations (moderators)

<!-- -   enticement lower nait toal correlations from 0.25 to .14 same with expertise -->

```{r enticement 2 corr}
corr_mod(m, correlations2)
```

### Marginal contrasts with Type

```{r enticement 2 model type load}
#| cache: false
 
m_type <- readRDS("models/ZOIB/ModelEnticement_2_ZOIB_type.rds")
```

```{r enticement 2 type model analysis}
params_table(m_type)
summary(m_type, robust = TRUE)
# performance::performance(m)
```

::: panel-tabset
#### Effect of Relevance

```{r enticement 1 est cont Releance with type }
#| message: false
#| warning: false

estimate_contrasts(m_type, contrast = "Relevance", by=c("Gender","Type"), backend = "emmeans") 
```

#### Effect of Condition

```{r enticement 2 est cont condition with Type }
#| message: false
#| warning: false

estimate_contrasts(m_type, contrast = "Condition", by=c("Gender", "Type"), backend = "emmeans") 
```

#### Effect of Condition depending on congruency

```{r enticement  2 type est cont}
estimate_contrasts(m_type, contrast = "Condition", by=c("Gender", "Type", "ConditionBelief"), backend = "emmeans")
```
:::

## Valence

```{r valence 2 by condition belief plot }
df2 |> 
  ggplot(aes(x = Gender, y = Valence, fill = ConditionBelief)) +
  geom_violin(position = position_dodge(width = 1), alpha = 0.7, trim = FALSE) +
  stat_pointinterval(position = position_dodge(width = 1),point_size = 1.5) +
  facet_grid( ~ Condition) +
  scale_fill_manual(values = c("True" = "#E66100", "False" = "#5D3A9B")) +
  theme_minimal(base_size = 14) +
  labs(title = "Valence by Gender × Belief × Condition", subtitle ="Study 2", x = "Gender", y = "Arousal",fill = "Condition Belief")
```

```{r valence 2 model load}
#| cache: false
 
m <- readRDS("models/ZOIB/ModelValence_2_ZOIB.rds")
```

```{r valence 2 model analysis}
params_table(m)
summary(m, robust = TRUE)
# performance::performance(m)
```

### Marginal Contrasts

::: panel-tabset
#### Effect of Relevance

```{r valence 1 est cont relevance}
#| message: false
#| warning: false

estimate_contrasts(m, contrast = "Relevance", by="Gender", backend = "emmeans") 
```

#### Effect of Condition

```{r valence 1 est cont condition }
#| message: false
#| warning: false

estimate_contrasts(m, contrast = "Condition", by="Gender", backend = "emmeans") 
```

#### Effect of Condition Depending on congruency

```{r valence 2 est cont}
estimate_contrasts(m, contrast = "Condition", by=c("Gender", "ConditionBelief"), backend = "emmeans")
```

```{r valence 2 model plot}
#| message: false
#| warning: false

pred_v2 <- modelbased::estimate_means(m, by=c("Gender", "Condition", "ConditionBelief"), backend = "emmeans") |>
  as.data.frame()

pd <- data.frame(label=c("pd = 100%", "pd = 100%", "pd = 99.96%"),
                 Gender = c("Male", "Female", "Male"),
                 ConditionBelief = c("Congruent", "Congruent", "Incongruent"),
                 y =c(0.65, 0.65, 0.62))


pred_v2 |>
  mutate(Gender = fct_relevel(Gender, "Male", "Female"),
         ConditionBelief = fct_recode(ConditionBelief, "Congruent" = "True", "Incongruent" = "False"),
         ConditionBelief = fct_relevel(ConditionBelief, "Congruent", "Incongruent")) |> 
  ggplot(aes(x=ConditionBelief, y=Probability)) +
    geom_hline(yintercept=0, color="darkgrey") +
  geom_line(aes(group=Condition, color=Condition), position = position_dodge(width=0.2), alpha=0.8, linewidth=0.2) +
  geom_pointrange(aes(ymin = CI_low, ymax=CI_high, color=Condition), position = position_dodge(width=0.2), size=0.2)+
  geom_text(data=pd, aes(y=y, label = label), hjust=0.5, size = 3.5) +
  geom_rect(data=data.frame(Probability=0.1, Gender=as.factor("Male"), ConditionBelief="Congruent"),
            aes(xmin = 0.8, xmax = 1.2,ymin=0.43, ymax=0.62), color="#8BC34A", alpha=0, linewidth = 1.2) +
  geom_rect(data=data.frame(Probability=0.1, Gender=as.factor("Female"), ConditionBelief="Congruent"),
            aes(xmin = 0.8, xmax = 1.2,ymin=0.43, ymax=0.62), color="#8BC34A", alpha=0, linewidth = 1.2) +
  facet_grid(~Gender, switch = "y") +
  scale_y_continuous(limits=c(0, 1), labels=scales::percent) +
  scale_color_manual(values=c("AIGenerated"="#2196F3", "Photograph"="#F44336")) +
  theme_minimal() +
    theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        axis.text.y = element_text(size = 8),
        strip.placement = "outside",
        strip.background.x = element_rect(fill=c("lightgrey"), color=NA),
        strip.text.x = element_text(size = 10, face= "bold"),
        strip.text.y = element_text(size = 10),
        axis.text.x = element_text(hjust=1, vjust=1.1, size=9, color="black", face = "bold"),
        legend.text = element_text(size = 10),
        legend.position = "bottom") +
  labs(color="Images presented as:")
```
:::

### Inter-individual Variability

::: panel-tabset
#### Random effects

```{r valence 2 d_vour}
m <- modelbased::estimate_grouplevel(m)
table_dvour(m)
```

#### Participant effects

```{r valence 2 ppt effects}
p_dvour(m, colors2)
```

:::

### Correlations (moderators)

```{r valence 2 corr}
corr_mod(m, correlations2)
```

### Marginal contrasts with Type

```{r valence  2 model type load}
#| cache: false
 
m_type <- readRDS("models/ZOIB/ModelValence_2_ZOIB_type.rds")
```

```{r valence 2 type model analysis}
params_table(m_type)
summary(m_type, robust = TRUE)
# performance::performance(m)
```

::: panel-tabset
#### Effect of Relevance

```{r valence 1 est cont relevance with type }
#| message: false
#| warning: false

estimate_contrasts(m_type, contrast = "Relevance", by=c("Gender", "Type"), backend = "emmeans") 
```

#### Effect of Condition

```{r valence  1 est cont condition with Type }
#| message: false
#| warning: false

estimate_contrasts(m_type, contrast = "Condition", by=c("Gender", "Type"), backend = "emmeans") 
```

#### Effect of Condition depending on congruency

```{r valence  2 type est cont}
estimate_contrasts(m_type, contrast = "Condition", by=c("Gender", "Type", "ConditionBelief"), backend = "emmeans")
```
:::

